---
title: "Build an R Package"
output:  
  html_document:  
    keep_md: true  
params:
  dtype: details
  ptitle: TRUE
  pbackground: TRUE
  number: 1
  casename: "cs-01"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

You are leaving your employer, and they have asked you to put together your key datasets and functions that you have developed over your employment into a well-documented R package.  If you build this package and place it on GitHub, then you will have access to all of your work as well.

## Tasks

```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}

cat("
<style>
ul {
   color: black;
   list-style-type: none;
   list-style-position: outside;

}

</style>
")
```

* [] Clean up your scripts from this semester into a set of functions.
    * [] Add roxygen comments
    * [] Build a data comments file for each dataset.
* [] Add a README.md that provides a short introduction to your package
* [] Push your package to GitHub
* [] Have your teacher review your GitHub repository

    
    
## Reading

* o [roxygen2 guide](https://support.rstudio.com/hc/en-us/articles/200532317-Writing-Package-Documentation){target="blank"}
* o [R packages](http://r-pkgs.had.co.nz/){target="blank"}
* o [Quick R package video](https://www.youtube.com/watch?v=9PyQlbAEujY){target="blank"} - Use `devtools::create("pathtopackage")` is needed before `load_all()` will work as he says.
* o [Packages on GitHub](http://kbroman.org/pkg_primer/pages/github.html){target="blank"}