---
title: "Runners and Goals"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

The New York Times published an [article](https://www.nytimes.com/2014/04/23/upshot/what-good-marathons-and-bad-investments-have-in-common.html?rref=upshot&_r=1) on some weird facts about issues that we have with setting goals.  They built a great graphic showing interesting characteristics in the distribution of running times. The data can be found [here](http://faculty.chicagobooth.edu/george.wu/research/marathon/data.htm). I have provided a [direct download link](https://www.dropbox.com/s/wq9e3wqzow500uo/master_marathon.csv?dl=1) to the full data as well. You might want to use the smaller randomly sampled data set of [1 million observations](https://www.dropbox.com/s/dp80lkd1n89gzma/master_marathon_1m.csv?dl=1) or [100k observations](https://byuistats.github.io/M335/data/runners_100k.csv).

## Your Challenge

We have a few challenges before us today. Use the full 1.5 hours to build the cleanest code and clearest presentation of your results. 

1. Recreate their graphic as close as you can using the skills you have developed this semester.  
2. Create a graphic that shows the relationship between times and the ages of the runners.
3. Examine the variables and create a novel graphic of your own.

```{r, eval=FALSE}
pacman::p_load(tidyverse, ggthemes)
dat <- read_csv("https://www.dropbox.com/s/wq9e3wqzow500uo/master_marathon.csv?dl=1")
# If you can't handle the full data set then use the following.
dat <- read_csv("https://www.dropbox.com/s/dp80lkd1n89gzma/master_marathon_1m.csv?dl=1")
#or
dat <- read_csv("https://byuistats.github.io/M335/data/runners_100k.csv")

```

```{r, include=FALSE,eval=FALSE}
dat %>%
  sample_n(1000000) %>%
  write_csv("master_marathon_1m.csv")

```


## Hints

Make sure to demonstrate quality and your skill set by using the three objectives. Don't worry about getting everything done perfectly. Remember, I am evaluating your profficency to use the coding tools taught in this class and your ability to create clean visualizations.

<!-- http://faculty.chicagobooth.edu/george.wu/research/marathon/data.htm -->
<!-- https://www.nytimes.com/2014/04/23/upshot/what-good-marathons-and-bad-investments-have-in-common.html?rref=upshot&_r=1 -->
<!-- http://tinlizzie.org/histograms/ -->
