---
title: "The Growth of Walmart"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Walmart Growth Visualization

Walmart's growth is astounding.  It may be the last giant in the "brick and mortar" business[^1] story ever. Our friends at [excelcharts.com](https://excelcharts.com/) have made some [nice graphics showing the spatial and temporal patterns of Walmart's growth](https://excelcharts.com/animation-small-multiples-growth-walmart-excel-edition/). We can't let Excel build such amazing graphics without a challenge from R!

We have a [Walmart_store_openings.csv](https://byuistats.github.io/M335/data/Walmart_store_openings.csv) file that we can use to build our visualizations.  You could use the `?state` object to see the data to use to get the colors correct and maybe could use `maps::us.cities` to get populations for cities.

## Your Challenge

We have a few challenges before us today. Use the full hour to build the cleanest code and most lucid presentation of your results. 

1. Recreate one of their graphics as close as you can using the skills you have developed this semester.  
2. After recreating their graphic, add a new feature or element to make it "better."
3. Examine the variables and create an original graphic of your own.


```{r, eval=FALSE}
pacman::p_load(tidyverse, ggthemes)
dat <- read_csv("https://byuistats.github.io/M335/data/Walmart_store_openings.csv")


```

## Hints

Make sure to demonstrate quality and your skill set by using the three objectives. Don't worry about getting everything done perfectly. Remember, I am evaluating your proficiency to use the coding tools taught in this class and your ability to create clear visualizations.

[^1]: It now has a significant online presence as well.  Amazon is pushing Walmart more than any other business has been able to challenge in the past.