---
output:
  xaringan::moon_reader:
    css: default
    lib_dir: externals
    nature:
      ratio: 16:9
      highlightLanguage: r
      highlightStyle: tomorrow-night-bright
      highlightLines: true
      countIncrementalSlides: false
params:
  day: 9
  ptitle: true
  pbackground: true
  dtype: "none"
---

---
class: center, middle, inverse

# Data Import
### J. Hathaway



```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(knitr)
library(stringr)
library(webshot)

invisible(purl("../backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")


# case study completed
cso <- ceiling(params$day/2) - 1
csn <- ceiling(params$day/2) 

casename_old <-  paste0("cs-", str_pad(cso, 2, "left", "0"))
casename_new <-  paste0("cs-", str_pad(csn, 2, "left", "0"))

link_old <- paste0("[Case Study ", cso, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_old,"-",""), "_details.html)")
link_new <- paste0("[Case Study ", csn, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_new,"-",""), "_details.html)")

# How did we do?
hdwd <- "[How did we do?](https://github.com/BYUI335/M335_HathawayJ/issues)"

# current task
# 
taskname <- paste0("task-", str_pad(params$day, 2, "left", "0"))
link_task <- paste0("[Task ", params$day, "](https://byuistats.github.io/M335/class_tasks/", str_replace(taskname,"-",""), "_details.html)")
```



```{r nextone, include=FALSE, cache=TRUE}
vday <- params$day - 1
vlink <- paste0("http://www.perceptualedge.com/example", vday, ".php")
vimage <- paste0("dayshot_", vday, ".png")
webshot(vlink, paste0("docs/presentations_class/images/", vimage), cliprect = "viewport")

titlelink <- paste0('background-image: url("images/', vimage, '")')

```



---
`r titlelink`
background-position: 50% 50%
class: center, bottom


# [Visualization of the Day](`r vlink`)


---
class: center, middle, inverse


# Review


---
class: center, middle



```{r csold, ref.label=casename_old, echo=FALSE, include=FALSE }
# For case study due last Saturday
```


`r title.text`

`r link_old`
   
   
`r hdwd`

--

```{r csnew, ref.label=casename_new, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_new`

--

```{r task, ref.label=taskname, echo=FALSE, include=FALSE }
# For current task that is due
```

`r title.text`
`r link_task`


```{r stuff, echo=FALSE}
unlink("temp")
```

---
class: center, middle, inverse

# Importing Data


---
class: middle


# Class Board Concept

## Write this chunk of code out in an English sentence to your grandma.

```{r ddndnddd,eval=FALSE}
read_rds(gzcon(url("https://github.com/.../Dart_Expert.RDS")))
```

---
class: middle


## Now write out the code in piped format

--

```{r dkdkdkjfkjdl333, echo=TRUE, eval=FALSE}
"https://github.com/byuistats/.../Dart_Expert_Dow_6month_anova.RDS" %>%
```

--

```{r dkdkdkjfkjdl333a, echo=TRUE, eval=FALSE}
  url() %>%
```

--

```{r dkdkdkjfkjdl333b, echo=TRUE, eval=FALSE}
  gzcon() %>%
```

--


```{r dkdkdkjfkjdl333c, echo=TRUE, eval=FALSE}  
  read_rds()
```





---

# What is `tempfile()` doing?

--

Run the following line and look at `bob`.  *What is it?*

```{r bbb13, eval=FALSE}
bob <- tempfile()

```

*Why would we want to use a `tempfile`?

--

```{r bbb13a, eval=FALSE}
download("https://github.com/byuistats/.../Dart_Expert_Dow_6month_anova.xlsx", bob, mode = "wb")

```

--


```{r bbb13b, eval=FALSE}
dxlsx <- read_xlsx(bob)
```

--

### Note that I am trying to save you from storing large data files in your Git repository.


---

The data import packages


## haven package

http://haven.tidyverse.org

## readxl package

http://readxl.tidyverse.org

## downloader package

[Just a wrapper around `download.file()`](https://github.com/wch/downloader/blob/master/R/download.r)

---

## Reading Files

--

### Describe in your task 9 readme what R is doing when you use a function like `read.csv()` or `read_csv()` without using the word `read`.  Try to be [succint](https://www.google.com/search?q=succint&oq=succint&aqs=chrome..69i57j0l5.2407j1j7&sourceid=chrome&ie=UTF-8).

#### When you are done push your file to GitHub.

--

## What words did we use to describe the process?

--

## What does [parse](https://www.google.com/search?ei=8BFpWtz6ApC4jwOLsa2ABQ&q=define+parse&oq=define+parse&gs_l=psy-ab.3..0i67k1j0l3j0i10k1j0l5.5615.7641.0.7785.12.12.0.0.0.0.134.1376.2j10.12.0....0...1c.1.64.psy-ab..0.12.1374...35i39k1j0i131k1j0i131i67k1j0i131i20i264k1j0i20i264k1.0.jsMRPqAjg-Q) mean?



---

# Reading in ASCII data as text

--

## Using read_lines() from `library(readr)`

--

```{r fishface1, eval=FALSE}
csvlines <- read_lines("https://github.com/byuistats/data/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.csv")
```

--

```{r fishface2, eval=FALSE}
mdlines <- read_lines("https://byuistats.github.io/M335/class_tasks/task09_details.md")
```


---

# Connecting to Databases

[db.rstudio.com](http://db.rstudio.com)
