---
title: "Moving Time Part I"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      lib_dir: externals
      keep_md: true
      incremental: true
      theme: black
      highlight: espresso
      center: true
      code_folding: hide
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        maxScale: 3
        margin: 0
params:
  day: 15
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(knitr)
library(stringr)

invisible(purl("../backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")


# case study completed
cso <- ceiling(params$day/2) - 1
csn <- ceiling(params$day/2) 

casename_old <-  paste0("cs-", str_pad(cso, 2, "left", "0"))
casename_new <-  paste0("cs-", str_pad(csn, 2, "left", "0"))

link_old <- paste0("> - [Case Study ", cso, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_old,"-",""), "_details.html)")
link_new <- paste0("> - [Case Study ", csn, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_new,"-",""), "_details.html)")

# How did we do?
hdwd <- "> - [How did we do?](https://github.com/BYUI335/hathaway)"

# current task
# 
taskname <- paste0("task-", str_pad(params$day, 2, "left", "0"))
link_task <- paste0("> - [Task ", params$day, "](https://byuistats.github.io/M335/class_tasks/", str_replace(taskname,"-",""), "_details.html)")

# Review
```


# Review

```{r csold, ref.label=casename_old, echo=FALSE, include=FALSE }
# For case study due last Saturday
```

`r title.text`
`r link_old`
`r hdwd`


```{r csnew, ref.label=casename_new, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_new`


```{r task, ref.label=taskname, echo=FALSE, include=FALSE }
# For current task that is due
```

`r title.text`
`r link_task`


```{r stuff, echo=FALSE}
unlink("temp")
```

# Settling In

## Socrative Quiz

> - [Socrative Quiz on Time](https://socrative.com): **BYUICLASS**

## R-Studio Connect and Interaction

Time to set up our R-Studio to share interactive documents.

>- shiny.byui.edu:3939 in R-Studio

Viewing on the website.

>- view with shiny.byui.edu



## library(DT) - DataTables

Make a new Rmd file that just has the following in it (including the yaml)

```{r bob, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r bob2, eval=FALSE}
library(DT)
datatable(iris)
```

Putting information in your file [My interactive](https://shiny.byui.edu/connect/#/apps/3/access)




## Remember the Goal

"The most exciting phrase to hear in science, the one that heralds new discoveries, is not 'Eureka!' but 'That's funny...'" -Isaac Asimov

> - [Remembering Good Principles](https://youtu.be/fSgEeI2Xpdc)
> - [Rauser view on time and data](https://www.youtube.com/embed/coNDCIMH8bk?start=628) - 10:28 to 17:50

> - [Remembering the question](https://www.youtube.com/watch?v=-3dw09N5_Aw) - First 10 minutes
>    - Correlation does not imply causation... The most popular defense of tiny minds in the face of uncomforatable evidence.
>    - You are rewarded for finding answers to the "that's funny" statements.
> - [Statistical Tests](https://www.youtube.com/embed/5Dnw46eC-0o)

