---
title: "Understanding Time (Applications)"
author: J. Hathaway
params:
  day: 16
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

if (params$day %% 2 == 0) md_intro_format <- "even_intro_format.Rmd"
if (params$day %% 2 == 1) md_intro_format <- "odd_intro_format.Rmd"

```

```{r child=md_intro_format}

```



# Class Activity

## The Changers (1)

> - floor_date(), 
> - round_date(), and 
> - ceiling_date()
> - force_tz()
> - with_tz()
> - https://cran.r-project.org/web/packages/lubridate/vignettes/lubridate.html
>    - Use `Sys.timezone(location = TRUE)` or `OlsonNames()` to see a list of timezones
> - [Nice reading on lubridate](https://blog.exploratory.io/5-most-practically-useful-operations-when-working-with-date-and-time-in-r-9f9eb8a17465)


## Challenge

Use `round_date()`, `ceiling_date()`, `floor_date()`, `force_tz()`, and `with_tz()` to answer the following questions.

> 1. Tell me what quarter this value is in if we are reporting quarters by the starting month of the quarter. While the time is recorded in UTC it is a transaction that happened in the mountain time zone.

2. Now suppose that the time read into R as UTC but that you know those times are actually recorded in the mountian time zone.  Repeat item 1. 

```{r fishface22, eval=FALSE, echo=TRUE}
library(lubridate)
x <- ymd_hms("2009-07-01 2:01:59.23")
```


## The Walmart March Visualization

> - [Small multiples and time](http://excelcharts.com/wp-content/uploads/2012/06/walmart-growth-micromaps1.png)
> - [Without spatial](http://excelcharts.com/wp-content/uploads/2012/06/walmart-reorderable-matrix.png)

## The Walmart Challenge

> 1. **Recreate this graphic**
> 2. **Propose a different graphic**

**The second link has the data**

> - [Without spatial](http://excelcharts.com/wp-content/uploads/2012/06/walmart-reorderable-matrix.png)
> - [Walmart Openings csv](https://byuistats.github.io/M335/data/Walmart_store_openings.csv)
> - `?state` to see the data to use to get the colors correct.

# Making new R package friends

## The challenge

> 1. Pick one of the R packages on the following slide
> 2. Read material on the R package
> 3. Build a working script that demonstrates the use of the R package.
> 4. Write up a short presentation on the package to show the class.

## The packages

> - [rio: The double click of data import](https://cran.r-project.org/web/packages/rio/vignettes/rio.html#data_import)
> - [janitor: making the cleaning easy](https://github.com/sfirke/janitor)
> - [tidytext: helps for text mining](https://github.com/juliasilge/tidytext)
> - [fst: yes it is fast](http://www.fstpackage.org/)
> - [glue: why should we paste](https://github.com/tidyverse/glue)
> - [reinstallr: getting your packages back](https://github.com/calligross/reinstallr)
> - [multidplyr: we need more than one dplyr?](http://www.business-science.io/code-tools/2016/12/18/multidplyr.html)
> - [skimr: pipeable summary statistics](https://github.com/ropenscilabs/skimr)
> - [fs: file system interface](https://github.com/r-lib/fs)






