---
title: "Getting control of Factors"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      lib_dir: externals
      keep_md: true
      incremental: true
      theme: black
      highlight: espresso
      center: true
      code_folding: hide
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        maxScale: 3
        margin: 0
params:
  day: 11
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(knitr)
library(stringr)

invisible(purl("../backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")


# case study completed
cso <- ceiling(params$day/2) - 1
csn <- ceiling(params$day/2) 

casename_old <-  paste0("cs-", str_pad(cso, 2, "left", "0"))
casename_new <-  paste0("cs-", str_pad(csn, 2, "left", "0"))

link_old <- paste0("> - [Case Study ", cso, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_old,"-",""), "_details.html)")
link_new <- paste0("> - [Case Study ", csn, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_new,"-",""), "_details.html)")

# How did we do?
hdwd <- "> - [How did we do?](https://github.com/BYUI335/hathaway)"

# current task
# 
taskname <- paste0("task-", str_pad(params$day, 2, "left", "0"))
link_task <- paste0("> - [Task ", params$day, "](https://byuistats.github.io/M335/class_tasks/", str_replace(taskname,"-",""), "_details.html)")


```{r csold, ref.label=casename_old, echo=FALSE, include=FALSE }
# For case study due last Saturday
```

# Review

`r title.text`
`r link_old`
`r hdwd`


```{r csnew, ref.label=casename_new, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_new`

```{r task, ref.label=taskname, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_task`

# Discussing Use Cases

## Call Center all

Who can tell the story of the call center data visualizations?  

> - [reading](http://biostat.mc.vanderbilt.edu/wiki/pub/Main/RafeDonahue/fscipdpfcbg_currentversion.pdf){target="blank"}

Of course, I was told the mean time to closure was some number of minutes, either 2 or 20 or 200 or something, I forget; it really doesn't matter for this discussion. They told me the mean, so naturally I asked for the raw, atomic-level data. 

## The data dive

- They gave me the data: a printout from an SQL routine that told me, accurate to twenty decimal places (I am not making this up!), the mean time to closure.
    - No, I need the data that you used to get these means; do you have that data?

- After several weeks, I was given a data set with hundreds of call durations.
    - Do you have the start and stop times from which you calculated these durations, the actual times the calls came in and when the cases were opened and closed?

- After several more weeks, I finally got the data: among other things, start and
stop times for each of the calls. 

## The call center data graphics

> - [All Calls](callcenter_all.png){target="blank"}
> - [Contractor Calls](callcenter_contract.png){target="blank"}
> - [Full-Time Calls](callcenter_fulltime.png){target="blank"}

#  Factoring in control

## Using Factors to improve communication

**Now that we have learned about factors let's take some time to fix our Case Study 5 work.**

>  1. Let's correctly sort our x-axes and then include both bars when we are making bar plots.
>  2. Let's fix our axis labels using legends.
>  3. Is there something better we can do than bar-plots?


## Your code or My code

If your code from case study 5 has enough to address the questions you can use your own code.  If not let's use mine.

> - [Hathaway Code for Case Study 5](https://byuistats.github.io/M335/presentations_class/restaurants_idaho.html)


## Sorting and Including Factor Levels

**with tidyr and dplyr**

> - `complete(nesting(SUBTYPE, Year), County, fill = list(value = 0, pop = 0, n = 0))`

**with ggplot2**

> - `scale_x_discrete(drop = FALSE)`
> - `scale_size_continuous(breaks = c(1, 3, 5, 8, 10), range = c(5, 8), guide = "none")`


## Fixing axes

> - `guides(color = guide_legend(override.aes = list(size = 5)))`
> - ` theme(panel.grid.minor = element_blank(), axis.text.x = element_text(angle = 35, vjust = 1, hjust = 1), legend.position = "bottom")`


## Moving beyond bar plots

What is the problem with bar plots?




