---
title: "Ode to Tidy"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      lib_dir: externals
      keep_md: true
      incremental: true
      theme: black
      highlight: espresso
      center: true
      code_folding: hide
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        maxScale: 3
        margin: 0
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
```

# Review

## Class Review Concept

> - Class Task 8: Create a table of the DJIA returns with months on the rows and years in the columns ("spread" the data)

Can a few people write example code to get this done?  Can the others that got it done using `spread()` help those that haven't made it that far?

## Review Timelines and Course Deliverables

> - [Semester Leadership and Project](https://byuistats.github.io/M335/tasklist.html)
> - [Semester Competencies](https://byuistats.github.io/M335/syllabus.html#grading_scale)

## Case Study 4:  Combining Data

> - [I can clean your data](https://byuistats.github.io/M335/weekly_projects/cs04_details.html)

## Task 8: Why do people make messy columns?!?!

> - [Task Summary](https://byuistats.github.io/M335/class_tasks/task08_details.html)
> - [Who wants to show their work?](https://github.com/BYUI335)

# Data Wild West

## "Happy families are all alike; every unhappy family is unhappy in its own way." 

**-- Leo Tolstoy**

## "Tidy datasets are all alike, but every messy dataset is messy in its own way." 

**-- Hadley Wickham**

## "There is one glory of the sun, and another glory of the moon, and another glory of the stars: for one star differeth from another star in glory."

**-- Paul (1 Corinthians 15:41)**

## Really. How bad can it get?

> * [R for Data Science Case Study](http://r4ds.had.co.nz/tidy-data.html#case-study)
> * [Wrangling Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf)

# Tidy Data and Analysis

## Tidy

**There are three interrelated rules which make a dataset tidy:**

1. Each variable must have its own column.
2. Each observation must have its own row.
3. Each value must have its own cell.

## Data Challenge

Read in this building utility data that is not very happy!

* You want to use 
    * `col_datetime(format = "%m%.%d%.%Y %H:%M")` and 
    * `col_date(format = "%m%.%d%.%Y")` 
    when you use `read_csv()`.
* https://byuistats.github.io/M335/data/building_utility_values.csv

```{r, eval=FALSE}
util <- read_csv("https://byuistats.github.io/M335/data/building_utility_values.csv")
```

## First Challenge

> * keep building variables, time variables and water variables
> * Create a state variable  
> * separate enddate into year, month, and day (three separate columns) and keep the enddate column

## Second Challenge

Use `library(dplyr)`, `library(tidyr)`, and `library(ggplot2)` to address the following.

> * How many buildings do we have in each state?
> * Create a graphic that compares the total potable gallons of water used by building over time to check the consistency of the data.

## Third Challenge

> * Find out how many total potable water measurements we have for each building by year?
> * Match this table format below

|id_number |2004 |2005 |2006 |2007 |
|:---------|:----|:----|:----|:----|
|0000OB    |-    |0    |0    |0    |
|0012ZZ    |-    |0    |9    |3    |
|......    |...  |...  |..   |...  |
|1923ZZ    |-    |12   |12   |3    |

## Fourth Challenge

> * Use the `gather()` function so you can make a `facet_grid()` plot with the six different water variables shown for each building.  You will need a variable column with all six water columns gathered into it.
> * What unique issue do you notice?
