---
title: "Ethics in Data Science"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      lib_dir: externals
      keep_md: true
      incremental: true
      theme: black
      highlight: espresso
      center: true
      code_folding: hide
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        maxScale: 3
        margin: 0
params:
  day: 23
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(knitr)
library(stringr)

invisible(purl("../backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")


# case study completed
cso <- ceiling(params$day/2) - 1
csn <- ceiling(params$day/2) 

casename_old <-  paste0("cs-", str_pad(cso, 2, "left", "0"))
casename_new <-  paste0("cs-", str_pad(csn, 2, "left", "0"))

link_old <- paste0("> - [Case Study ", cso, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_old,"-",""), "_details.html)")
link_new <- paste0("> - [Case Study ", csn, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_new,"-",""), "_details.html)")

# How did we do?
hdwd <- "> - [How did we do?](https://github.com/BYUI335/hathaway)"

# current task
# 
taskname <- paste0("task-", str_pad(params$day, 2, "left", "0"))
link_task <- paste0("> - [Task ", params$day, "](https://byuistats.github.io/M335/class_tasks/", str_replace(taskname,"-",""), "_details.html)")

# Review
```


# Review

```{r csold, ref.label=casename_old, echo=FALSE, include=FALSE }
# For case study due last Saturday
```

`r title.text`
`r link_old`
`r hdwd`


```{r csnew, ref.label=casename_new, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_new`


# Clarifications on Mathematics

## Hathaway's Quote

Mathematics classes are ____________.

## The Fathers of Statistics (Fisher)

Statement from Fisher's first boss.

**when I first saw him in 1919 he was out of a job. Before deciding anything I wrote to his tutor at Caius college . . . about his mathematical ability. The answer was that he could have been a first class mathematician had he "stuck to the ropes" but he would not. That looked like the type of man we wanted.. . . I had only £200 and suggested he should stay as long as he thought that should suffice.. . . He reported to me weekly at tea at my house.. . . It took me a very short time to realize that he was more than a man of great ability, he was in fact a genius.**


## The Fathers of Statistics (Box)

**The investigator who hopes to revolutionize decision theory should observe and take part in the making of important decisions.** An appropriately chosen environment can suggest to such an investigator new theories or models worthy to be entertained. Mathematics artfully employed can then enable him to derive the logical consequences of his tentative hypotheses and his strategically selected environment will allow him to **compare these consequences with practical reality.** In this way he can begin an iteration that can eventually achieve his goal. 

## The Fathers of Statistics (Box)

**An alternative is to redefine such words as *experimental design* and *decision* so that mathematical solutions which do not necessarily have any relevance to reality may be declared optimal.**

**It requires among other things the wit to comprehend complicated scientific problems, the patience to listen, the penetration to ask the right questions, and the wisdom to see what is, and what is not, important.** 

## The Fathers of Statistics (Box on Fisher)

... **Why then did [Fisher] sometimes seem to refer so slightingly to mathematicians?** The answer I think is that his real target was "mathematistry." It is to make the distinction that the word is introduced here.

**Mathematistry is characterized by development of theory for theory's sake, which since it seldom touches down with practice, has a tendency to redefine the problem rather than solve it.** 

## The Fathers of Statistics (Tukey)

The most important maxim for data analysis to heed, and one which many statisticians seem to have shunned, is this: **"Far better an approximate answer to the right question, which is often vague, than an exact answer to the wrong question, which can always be made precise."** Data analysis must progress by approximate answers, at best, since its knowledge of what the problem really is will at best be approximate.

## The Fathers of Statistics (Tukey)

**Finally, we need to give up the vain hope that data analysis can be founded upon a logico-deductive system like Euclidean plane geometry (or some form of the propositional calculus) and to face up to the fact that data analysis is intrinsically an empirical science.** 

[Fun Video from Tukey on visualization](http://stat-graphics.org/movies/prim9.html)

```{r task, ref.label=taskname, echo=FALSE, include=FALSE }
# For current task that is due
```

`r title.text`
`r link_task`


```{r stuff, echo=FALSE}
unlink("temp")
```