---
title: "Getting Comfortable"
author: J. Hathaway
params:
  day: 20
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

if (params$day %% 2 == 0) md_intro_format <- "even_intro_format.Rmd"
if (params$day %% 2 == 1) md_intro_format <- "odd_intro_format.Rmd"

```

```{r child=md_intro_format}

```

# "Big" Data

## Scientists Vs. Analysts

> - Best way to differentiate a data scientist from a data analyst. 
>    - **Data Analyst:** If my tools and data can't answer a question, then the question doesn't get answered.
>    - **Data Scientist:** If my tools and data can't answer a question, then I go get better tools and data.

## Leaving your little computer

> - [The science is the idea and data moving](https://www.youtube.com/embed/Ewd5PXgLXlU?start=488)
> - [Big is different in many ways](https://www.youtube.com/embed/Ewd5PXgLXlU?start=690)

# Maps Vs. Variables

## What is wrong?

"Here, you can take that, that's the final map of the numbers," Trump said, according to Reuters.  "It's pretty good, right? The red is obviously us." [1](http://www.businessinsider.com/trump-2016-electoral-map-reuters-interview-xi-jinping-china-2017-4)

[Trump Map Tweet](../images/trump_map_tweet.png)

## How could we spatially depict the variable of interest?

- [Chloropleth Map](https://en.wikipedia.org/wiki/Choropleth_map)
- [Cartograms](https://en.wikipedia.org/wiki/Cartogram)
- [geofacets](https://hafen.github.io/geofacet/)

## geofacet challenge

**Use the geofacet package to build a map that depicts the important variables more than the spatial area.**

> - Will need to aggregate your data the state level.
> - Will need to use `install.packages("geofacet")` and the `facet_geo()` function.

[data](../data/nytimes_presidential_elections_2016_results_county.csv)

## Checking out some results

- Who has pushed their graphic?
- [Check these out](http://www.businessinsider.com/2016-election-results-maps-population-adjusted-cartogram-2016-11/#heres-the-basic-electoral-college-map-with-states-that-hillary-clinton-won-in-blue-and-states-that-donald-trump-won-in-red-assuming-that-trumps-narrow-lead-in-michigan-continues-to-hold-1)



