---
title: Data Import
author: J. Hathaway
params:
  day: 9
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

if (params$day %% 2 == 0) md_intro_format <- "even_intro_format.Rmd"
if (params$day %% 2 == 1) md_intro_format <- "odd_intro_format.Rmd"

```

# Becoming the Critic. {data-background=#e8d725}

```{r nextone}
vday <- params$day - 1
vlink <- paste0("http://www.perceptualedge.com/example", vday, ".php")
titlelink <- paste0('{data-background-iframe="', vlink, '"}')
```

## `r titlelink`

[Visualization of the Day](`r vlink`)


```{r child=md_intro_format}

```



# Importing Data {data-background=#e8d725}

## Board Activity

Write this chunk of code out in an English sentence to your grandma.

```{r ddndnddd,eval=FALSE, echo=TRUE}
read_rds(gzcon(url("https://github.com/.../Dart_Expert.RDS")))
```

> - Now write out the code in piped format

```{r dkdkdkjfkjdl333, echo=FALSE, eval=FALSE}
"https://github.com/byuistats/data/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.RDS" %>%
  url() %>% 
  gzcon() %>%
  read_rds()
```


## What is `tempfile()` doing?

Run the following line and look at `bob`.  *What is it?*

```{r bbb13, eval=FALSE}
bob <- tempfile()

```

* Why would we want to use a `tempfile`?


```{r bbb13a, eval=FALSE, echo=TRUE}
download("https://github.com/byuistats/.../Dart_Expert_Dow_6month_anova.xlsx", bob, mode = "wb")

```


```{r bbb13b, eval=FALSE, echo=TRUE}
dxlsx <- read_xlsx(bob)
```

**Note that I am trying to save you from storing large data files in your Git repository.**


# The data import packages {data-background=#e8d725}


## haven package

http://haven.tidyverse.org

## readxl package

http://readxl.tidyverse.org

## downloader package

[Just a wrapper around `download.file()`](https://github.com/wch/downloader/blob/master/R/download.r)

## Reading Files

**Describe in your task 9 readme what R is doing when you use a function like `read.csv()` or `read_csv()` without using the word `read`.  Try to be [succint](https://www.google.com/search?q=succint&oq=succint&aqs=chrome..69i57j0l5.2407j1j7&sourceid=chrome&ie=UTF-8).**


#### When you are done push your file to GitHub.



## What words did we use to describe the process?

## What does [parse](https://www.google.com/search?ei=8BFpWtz6ApC4jwOLsa2ABQ&q=define+parse&oq=define+parse&gs_l=psy-ab.3..0i67k1j0l3j0i10k1j0l5.5615.7641.0.7785.12.12.0.0.0.0.134.1376.2j10.12.0....0...1c.1.64.psy-ab..0.12.1374...35i39k1j0i131k1j0i131i67k1j0i131i20i264k1j0i20i264k1.0.jsMRPqAjg-Q) mean?


# Reading in ASCII data as text {data-background=#e8d725}

## Using read_lines() from `library(readr)`


```{r fishface1, eval=FALSE, echo=TRUE}
csvlines <- read_lines("https://github.com/byuistats/data/raw/master/Dart_Expert_Dow_6month_anova/Dart_Expert_Dow_6month_anova.csv")
```

```{r fishface2, eval=FALSE, echo=TRUE}
mdlines <- read_lines("https://byuistats.github.io/M335/class_tasks/task09_details.md")
```

## Connecting to Databases

[db.rstudio.com](http://db.rstudio.com)

## Excel with Excel

> - http://altons.github.io/rstats/2015/02/13/quick-intro-to-xlconnect/
> - https://github.com/miraisolutions/xlconnect

# Semester Project & Class {data-background=#e8d725}

## Discuss Example Code

Let's look at an example set of scripts that get at what I was trying to say in Task 8.

* https://github.com/hathawayj/datasus
<<<<<<< HEAD
    * https://github.com/hathawayj/datasus/blob/master/sinasc_hospital_artifacts.R
    * https://github.com/hathawayj/datasus/blob/master/sinasc_hospital_explore.R
=======
>>>>>>> 3555fbbcd42e43308a527a106f7c819389108e06
* Why are we doing the semester project?
* What parts of this class do you think will be relevant to your future jobs?
* What could we do to improve the experience in the first five weeks?

## Time to work on Case Studies, Tasks, and semester projects.