---
title: "Getting Comfortable"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      lib_dir: externals
      keep_md: true
      incremental: true
      theme: black
      highlight: espresso
      center: true
      code_folding: hide
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        maxScale: 3
        margin: 0
params:
  day: 20
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(knitr)
library(stringr)

invisible(purl("../backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")


# case study completed
cso <- ceiling(params$day/2) - 1
csn <- ceiling(params$day/2) 

casename_old <-  paste0("cs-", str_pad(cso, 2, "left", "0"))
casename_new <-  paste0("cs-", str_pad(csn, 2, "left", "0"))

link_old <- paste0("> - [Case Study ", cso, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_old,"-",""), "_details.html)")
link_new <- paste0("> - [Case Study ", csn, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_new,"-",""), "_details.html)")

# How did we do?
hdwd <- "> - [How did we do?](https://github.com/BYUI335/hathaway)"

# current task
# 
taskname <- paste0("task-", str_pad(params$day, 2, "left", "0"))
link_task <- paste0("> - [Task ", params$day, "](https://byuistats.github.io/M335/class_tasks/", str_replace(taskname,"-",""), "_details.html)")
```

# Review

```{r csnew, ref.label=casename_new, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_new`


```{r task, ref.label=taskname, echo=FALSE, include=FALSE }
# For current task that is due
```

`r title.text`
`r link_task`


```{r stuff, echo=FALSE}
unlink("temp")
```

# Questions & Code

## Joseph's Question

Write out in a sentence what this code is doing. Make sure to catch the key points in your sentence

```{r p1, eval=FALSE}
dams_path <- "https://research.idwr.idaho.gov/gis/Spatial/DamSafety/dam.zip"
df <- tempfile(); uf <- tempfile()
download(dams_path, df, mode = "wb")
unzip(df, exdir = uf)
dams <- read_sf(uf)
file.remove(df); file.remove(uf)

```

## My old code

Try to write out what this is doing?


```{r p2, eval=FALSE}
#library(reshape) # this is needed for old code
gcam <- read.csv("instructor/facetus_pnnl/USTrellis_Example/CASCaDE_A2_Full.csv", stringsAsFactors = FALSE)
agcam <- subset(gcam[,c("scenario","region","input","sector",paste("X",seq(2005,2095,by=5),sep=""))],scenario=="GFDL_A2_RGCAM_medium,date=2012-26-11T18:22:24-05:00")
agcam <- subset(agcam,sector%in%c("resid cooling","resid heating","comm cooling","comm heating"))
agcam.m <- melt(data=agcam[,-1],id.var=c("region","input","sector"))
agcam.m$heat.cool <- gsub("resid ","",gsub("comm ","",agcam.m$sector))
agcam.c.split <- cast(data=agcam.m,region+heat.cool~variable,fun.aggregate=sum,value="value")
agcam.cooling <- subset(agcam.c.split,heat.cool=="cooling")[,-2]
agcam.heating <- subset(agcam.c.split,heat.cool=="heating")[,-2]
agcam.split <- list(heating=agcam.heating,cooling=agcam.cooling)
agcam.c <- cast(data=agcam.m,region~variable,fun.aggregate=sum,value="value")
tgcam <- subset(gcam[,c("scenario","region","input","sector","X2005")],scenario=="GFDL_A2_RGCAM_medium,date=2012-26-11T18:22:24-05:00")
tgcam <- subset(tgcam,sector%in%c("resid cooling","resid heating","comm cooling","comm heating"))
mtgcam <- cast(data=tgcam,region~sector,value="X2005",fun.aggregate=sum)

```

## My new code

```{r p3, eval=FALSE}
library(tidyverse)

gcamt <- read_csv("instructor/facetus_pnnl/USTrellis_Example/CASCaDE_A2_Full.csv")

gcamtt <- gcamt %>% 
  dplyr::filter(scenario=="GFDL_A2_RGCAM_medium,date=2012-26-11T18:22:24-05:00", 
         sector %in% c("resid cooling","resid heating","comm cooling","comm heating")) %>%
 # dplyr::mutate(skey = paste(region, input, sector, sep = "_")) %>%
  dplyr::select(-scenario, - Units) %>%
  tidyr::gather(key = year, value = energy,`1990`:`2095`, -region, - input, -sector) %>%
  dplyr::mutate(heat.cool = gsub("resid ","",gsub("comm ","",sector)))

gcam_totals <- gcamtt %>%
  group_by(region, year, heat.cool, sector) %>%
  summarise(energy = sum(energy)) %>% 
  ungroup()
```


# "Big" Data

## Scientists Vs. Analysts

> - Best way to differentiate a data scientist from a data analyst. 
>    - **Data Analyst:** If my tools and data can't answer a question, then the question doesn't get answered.
>    - **Data Scientist:** If my tools and data can't answer a question, then I go get better tools and data.

## Leaving your little computer

> - [The science is the idea and data moving](https://www.youtube.com/embed/Ewd5PXgLXlU?start=488)
> - [Big is different in many ways](https://www.youtube.com/embed/Ewd5PXgLXlU?start=690)

# Maps Vs. Variables

## What is wrong?

"Here, you can take that, that's the final map of the numbers," Trump said, according to Reuters.  "It's pretty good, right? The red is obviously us." [1](http://www.businessinsider.com/trump-2016-electoral-map-reuters-interview-xi-jinping-china-2017-4)

[Trump Map Tweet](../images/trump_map_tweet.png)

## How could we spatially depict the variable of interest?

- [Chloropleth Map](https://en.wikipedia.org/wiki/Choropleth_map)
- [Cartograms](https://en.wikipedia.org/wiki/Cartogram)
- [geofacets](https://hafen.github.io/geofacet/)

## geofacet challenge

Use the geofacet package to build a map that depicts the variables important more than the spatial area.

> - Will need to aggregate your data the state level.
> - Will need to use `install.packages("geofact")` and the `facet_geo()` function.

[data](../data/nytimes_presidential_elections_2016_results_county.csv")

## Checking out some results

- Who has pushed their graphic?
- [Check these out](http://www.businessinsider.com/2016-election-results-maps-population-adjusted-cartogram-2016-11/#heres-the-basic-electoral-college-map-with-states-that-hillary-clinton-won-in-blue-and-states-that-donald-trump-won-in-red-assuming-that-trumps-narrow-lead-in-michigan-continues-to-hold-1)