---
title: "Interactive Maps and Ending the Semester"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      lib_dir: externals
      keep_md: true
      incremental: true
      theme: black
      highlight: espresso
      center: true
      code_folding: hide
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        maxScale: 3
        margin: 0
params:
  day: 21
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(knitr)
library(stringr)

invisible(purl("../backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")


# case study completed
cso <- ceiling(params$day/2) - 1
csn <- ceiling(params$day/2) 

casename_old <-  paste0("cs-", str_pad(cso, 2, "left", "0"))
casename_new <-  paste0("cs-", str_pad(csn, 2, "left", "0"))

link_old <- paste0("> - [Case Study ", cso, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_old,"-",""), "_details.html)")
link_new <- paste0("> - [Case Study ", csn, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_new,"-",""), "_details.html)")

# How did we do?
hdwd <- "> - [How did we do?](https://github.com/BYUI335/hathaway)"

# current task
# 
taskname <- paste0("task-", str_pad(params$day, 2, "left", "0"))
link_task <- paste0("> - [Task ", params$day, "](https://byuistats.github.io/M335/class_tasks/", str_replace(taskname,"-",""), "_details.html)")

# Review
```


# Review

```{r csold, ref.label=casename_old, echo=FALSE, include=FALSE }
# For case study due last Saturday
```

`r title.text`
`r link_old`
`r hdwd`


```{r csnew, ref.label=casename_new, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_new`


```{r task, ref.label=taskname, echo=FALSE, include=FALSE }
# For current task that is due
```

`r title.text`
`r link_task`


```{r stuff, echo=FALSE}
unlink("temp")
```

# Finishing the Semester

## Semester Project Discussion

> - [Semester project](https://byuistats.github.io/M335/project.html)
> - ["Your flavor of .Rmd"](http://rmarkdown.rstudio.com/formats.html)

## Tracking Progress

> - Don't forget to keep track of your tasks.
> - Semester project should be moving along.
> - Check out week 13 work and make sure you are working on this.

## Completing your portfolio

Weeks 12 and 13 are going to take some work and will be the most rewarding of the class.  I am expecting that you will put in the time to make these parts of the class productive.

> - [Week 13](https://byuistats.github.io/M335/weekly_projects/cs13_details.html)

## Using Leaflet

Adding layers thoughtfully

> - [Here is my Task 21 and Case Study 11](https://shiny.byui.edu/connect/#/apps/106/access)
> - [Spatial Data Often becomes big data](https://blogs.esri.com/esri/arcgis/2017/10/17/strategies-to-effectively-display-large-amounts-of-data-in-web-apps/)
>    - [Firefly Cartography](https://adventuresinmapping.com/2016/10/17/firefly-cartography/)
