---
title: "Getting control of Factors"
author: J. Hathaway
params:
  day: 13
  ptitle: true
  pbackground: true
  dtype: "none"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

if (params$day %% 2 == 0) md_intro_format <- "even_intro_format.Rmd"
if (params$day %% 2 == 1) md_intro_format <- "odd_intro_format.Rmd"

```

# Thought for the day

## What I see: Greatness

<iframe width="900" height="500" src="https://www.youtube.com/embed/XcbSCnUXOkk" frameborder="0" allow="autoplay; encrypted-media" allowfullscreen></iframe>


## What you may think is happening.

<iframe width="900" height="500" src="https://www.youtube.com/embed/-KSryJXDpZo" frameborder="0" allow="autoplay; encrypted-media" allowfullscreen></iframe>


```{r child=md_intro_format}

```

# Discussing Use Cases

## Call Center all

Who can tell the story of the call center data visualizations?  

> - [reading](http://biostat.mc.vanderbilt.edu/wiki/pub/Main/RafeDonahue/fscipdpfcbg_currentversion.pdf){target="blank"}

Of course, I was told the mean time to closure was some number of minutes, either 2 or 20 or 200 or something, I forget; it really doesn't matter for this discussion. They told me the mean, so naturally I asked for the raw, atomic-level data. 

## The data dive

- They gave me the data: a printout from an SQL routine that told me, accurate to twenty decimal places (I am not making this up!), the mean time to closure.
    - No, I need the data that you used to get these means; do you have that data?

- After several weeks, I was given a data set with hundreds of call durations.
    - Do you have the start and stop times from which you calculated these durations, the actual times the calls came in and when the cases were opened and closed?

- After several more weeks, I finally got the data: among other things, start and
stop times for each of the calls. 

## The call center data graphics

> - [All Calls](callcenter_all.png){target="blank"}
> - [Contractor Calls](callcenter_contract.png){target="blank"}
> - [Full-Time Calls](callcenter_fulltime.png){target="blank"}

#  Factoring in control

## Using Factors to improve communication

**Now that we have learned about factors let's take some time to fix our Case Study 6 work.**

>  1. Let's correctly sort our x-axes and then include both bars when we are making bar plots.
>  2. Let's fix our axis labels and legends.
>  3. Is there something better we can do than bar-plots?


## Your code or My code

If your code from case study 6 has enough to address the questions you can use your own code.  If not let's use mine.

[Hathaway code](restaurant_data_build.R){target="blank"}



## Sorting and including factor levels

**[with tidyr and dplyr](http://www.imachordata.com/you-complete-me/)**

```{r bobobobbo, eval=FALSE, echo=TRUE}
complete()
```

**with ggplot2**

```{r, jojojoj, eval=FALSE, echo=TRUE}
scale_x_discrete(drop = FALSE)
scale_size_continuous(breaks = c(), range = c(), guide = "none")

```



## Fixing axes

```{r ghdhkjdkjdh,eval=FALSE, echo=TRUE}
guides(color = guide_legend(override.aes = list(size = 5)))
theme(panel.grid.minor = element_blank(), axis.text.x = element_text(angle = 35, vjust = 1, hjust = 1), legend.position = "bottom")

```











