---
title: "Finding names"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      lib_dir: externals
      keep_md: true
      incremental: true
      theme: black
      highlight: espresso
      center: true
      code_folding: hide
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        maxScale: 3
        margin: 0
params:
  day: 12
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(knitr)
library(stringr)

invisible(purl("../backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")


# case study completed
cso <- ceiling(params$day/2) - 1
csn <- ceiling(params$day/2) 

casename_old <-  paste0("cs-", str_pad(cso, 2, "left", "0"))
casename_new <-  paste0("cs-", str_pad(csn, 2, "left", "0"))

link_old <- paste0("> - [Case Study ", cso, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_old,"-",""), "_details.html)")
link_new <- paste0("> - [Case Study ", csn, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_new,"-",""), "_details.html)")

# How did we do?
hdwd <- "> - [How did we do?](https://github.com/BYUI335/hathaway)"

# current task
# 
taskname <- paste0("task-", str_pad(params$day, 2, "left", "0"))
link_task <- paste0("> - [Task ", params$day, "](https://byuistats.github.io/M335/class_tasks/", str_replace(taskname,"-",""), "_details.html)")

# Review


```{r csnew, ref.label=casename_new, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_new`

Let's talk about this case study and what is acheivable.

* Altered task: complete the task items or spend 2 hours trying to make it work.
    * Document the pseudo code you would use (it needs for loops and `str_` commands.
    * Describe the visualization you would have made.

## Mapping out the coding challenge

**In your tables:**

> - Read the task and write a one word statement of what you need to do
> - Mock up what your final data may need to look like (what columns do you need to make a good visualization)
> - Write pseudo code that would get you to an answer


```{r task, ref.label=taskname, echo=FALSE, include=FALSE }
# For current task that is due
```

`r title.text`
`r link_task`

## Class Task 12 (data)

```{r scripturedata, cache=TRUE, results=FALSE}
library(rio)
library(stringr)
library(stringi)
scriptures <- import("http://scriptures.nephi.org/downloads/lds-scriptures.csv.zip")
bm <- scriptures %>% filter(volume_short_title == "BoM")
```

## Class Task 12 (average)

```{r, eval=FALSE}

bm_counts <- bm %>% 
  group_by(verse_title, chapter_id, book_id, chapter_number, verse_number, book_title) %>% 
  summarise(word_count = stri_stats_latex(scripture_text)["Words"],
            charsword = stri_stats_latex(scripture_text)["CharsWord"],
            charswhite = stri_stats_latex(scripture_text)["CharsWhite"])

```

## Class Task 12 (finding Jesus)


```{r, eval=FALSE}
bm_locs <- bm$scripture_text %>% 
            str_locate_all(c("Jesus")) %>% 
            lapply(function(x) nrow(x)) %>%
            unlist()
sum(bm_locs)
```

# Loops for what?

## Making the loop (challenge)

**The challenge:**  Use the savior names list and write out how you would use a for loop to find/break this one verse into chunks to get an word count between each.

[2 Nephi 25:16](https://www.lds.org/scriptures/bofm/2-ne/25.16)

## Making the loop (code)

 * Now just use this verse to run your for loop

```{r, eval=FALSE}
verse <- read_lines("https://byuistats.github.io/M335/data/2nephi2516.txt")
names <- import("https://byuistats.github.io/M335/data/BoM_SaviorNames.rds")

```


# Making new R package friends

## The challenge

1. Pick one of the R packages on the following slide
2. Read material on the R package
3. Build a working script that demonstrates the use of the R package.
4. Write up a short presentation on the package.

## The packages

- [rio: The double click of data import](https://cran.r-project.org/web/packages/rio/vignettes/rio.html#data_import)
- [janitor: making the cleaning easy](https://github.com/sfirke/janitor)
- [tidytext: helps for text mining](https://github.com/juliasilge/tidytext)
- [fst: yes it is fast](http://www.fstpackage.org/)
- [glue: why should we paste](https://github.com/tidyverse/glue)
- [reinstallr: getting your packages back](https://github.com/calligross/reinstallr)
- [multidplyr: we need more than one dplyr?](http://www.business-science.io/code-tools/2016/12/18/multidplyr.html)


