---
title: " and the Critique"
author: J. Hathaway
params:
  day: 6
  ptitle: true
  pbackground: true
  dtype: "none"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

if (params$day %% 2 == 0) md_intro_format <- "even_intro_format.Rmd"
if (params$day %% 2 == 1) md_intro_format <- "odd_intro_format.Rmd"

```

# Becoming the Critic. {data-background=#e8d725}

```{r nextone}
vday <- params$day - 1
vlink <- paste0("http://www.perceptualedge.com/example", vday, ".php")
titlelink <- paste0('{data-background-iframe="', vlink, '"}')
```

## `r titlelink`

[Visualization of the Day](`r vlink`)


```{r child=md_intro_format}

```



# Providing Critiques and the Routine {data-background=#e8d725}

## A few critique examples

* [Mckay's](https://github.com/BYUI335/Davis_M/issues/5):  Notice how he responds that he has addressed the issues.
* [Aletha's Request](https://github.com/BYUI335/Pyeatt_A/issues/5):  Notice her request and the responses.
* [Hathaway's Example Response](https://github.com/BYUI335/Pyeatt_A/issues/7): Notice the formatting and references.


# Displaying multiple distributions {data-background=#e8d725}

## Clarity vs. Complication

Data can get complicated very fast. How do we provide depth of variability understanding without overwhelming the visualization user?

> * [violin plots](http://eamoncaddigan.net/dataviz/r/psych/2015/09/26/violin-plots/)
> * [beeswarm plots](https://github.com/eclarke/ggbeeswarm)
> * [letter-value boxplots](https://github.com/hadley/lvplot)

Another package that makes flipping the axes easier in ggplot -- [rotating axes](https://github.com/lionel-/ggstance)

> * [link to last presentation](day_5.html#/displaying-distributions-of-multiple-groups-for-decision-making)

## Clarity vs. Complication (2)

> - What do we know after looking at this plot?
> **How do we provide depth of variability understanding without overwhelming the visualization user?**


```{r cc1, echo=FALSE, fig.height= 3}
library(nycflights13)
library(tidyverse)
library(magrittr)
library(forcats)

flights %>% 
  group_by(carrier) %>% 
  summarise(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = fct_reorder(carrier, dep_delay), y = dep_delay)) +
  geom_col() +
  labs(x = "Airline Carrier Short Name", y = "Average Departure Delay", title = "Typical Delay of Flights by Airport") + theme_bw()

<<<<<<< HEAD
=======
```{r bob, evel=FALSE, echo=TRUE}
best_in_class <- mpg %>%
  group_by(class) %>%
  filter(row_number(desc(hwy)) == 1)
>>>>>>> 3555fbbcd42e43308a527a106f7c819389108e06
```



Remember, data can get complicated very fast. 


```{r, echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
pacman::p_load(ggbeeswarm, lvplot)

```


## Distribution background

* [violin plots](http://eamoncaddigan.net/dataviz/r/psych/2015/09/26/violin-plots/)
* [beeswarm plots](https://github.com/eclarke/ggbeeswarm)
* [letter-value box-plots](https://github.com/hadley/lvplot)
* Another package that makes flipping the axes easier in ggplot -- [rotating axes](https://github.com/lionel-/ggstance)


## Histograms (1)

What don't we like about this plot?

```{r bbbb3, fig.height=4, fig.width=8, cache=TRUE}
# plot code for histograms

<<<<<<< HEAD
flights %>% 
    ggplot(aes(x = dep_delay)) +
    facet_wrap(~carrier) +
    geom_histogram(bins = 150, color = "white") +
    coord_cartesian(xlim = c(-50, 250)) +
    theme_bw()

```


## Histograms (2)

* What changed in this histogram?
* What don't we like about this plot?
=======
> 1. Run this line of code below
> 2. Look at the errors (`problems(challenge)`), the `head()`, and `tail()` of your `challenge` object.  What formats should they be?
> 3. Now review [11.4.2 of our textbook](http://r4ds.had.co.nz/data-import.html#problems) and fix the read in.

```{r vle3, eval=FALSE, echo=TRUE}
challenge <- read_csv(readr_example("challenge.csv"))
```
>>>>>>> 3555fbbcd42e43308a527a106f7c819389108e06

```{r bbbbb5, fig.height=4, fig.width=8, cache=TRUE}
# plot code for histograms

flights %>% 
    ggplot(aes(x = dep_delay)) +
    facet_wrap(~carrier, scales = "free_y") +
    geom_histogram(bins = 150, color = "white") +
    coord_cartesian(xlim = c(-50, 250)) +
    theme_bw()

```

## Boxplots

* What don't we like about this plot?
* How hard is it to explain?

```{r bbbbbb444, fig.height=4, fig.width=8, cache=TRUE}

gg_base <- flights %>%
  ggplot(aes(x = carrier, y = dep_delay)) +
    coord_cartesian(ylim = c(-50, 250)) +
    theme_bw()
# Now add varied distribution geoms

gg_base + geom_boxplot() 
```

## Violin plots

* What don't we like about this plot?
* How hard is it to explain?

```{r violin, fig.height=4, fig.width=8, cache=TRUE}

# Now add varied distribution geoms
gg_base + geom_violin()

```

## Beeswarm plots (1)

* What don't we like about this plot?
* How hard is it to explain?

```{r beeswarm, fig.height=4, fig.width=8, cache=TRUE}
# Now add varied distribution geoms
library(ggbeeswarm)
gg_base + geom_quasirandom(alpha = .6, size = .75)

```

<<<<<<< HEAD
## Beeswarm plots (1)

* What don't we like about this plot?
* How hard is it to explain?

```{r beeswarm2, fig.height=4, fig.width=8, cache=TRUE}
# Now add varied distribution geoms
library(ggbeeswarm)
gg_base + geom_quasirandom(alpha = .6, size = .75) + 
  coord_cartesian(ylim = c(-50, 500)) 

=======
## My Code Solution

```{r newname_code, eval=FALSE, echo=TRUE}
library(ggrepel)
library(viridis)

best_in_class <- mpg %>% 
  group_by(class) %>% 
  filter(row_number(desc(hwy)) == 1)

ggplot(mpg, aes(displ, hwy)) +
  geom_point(aes(colour = class), size = 3) +
  geom_point(size = 1.5, data = best_in_class, color = "white") +
  geom_text_repel(aes(label = model, colour = class), 
                  data = best_in_class, show.legend = FALSE, 
                  nudge_x = -1, nudge_y = -2) +
  theme_bw() + theme(panel.grid.minor = element_blank()) +
  scale_color_viridis(discrete = TRUE) + 
  labs(x = "Engine displacement", y = "Miles per gallon (highway)", 
       color = "Vehicle type")
>>>>>>> 3555fbbcd42e43308a527a106f7c819389108e06
```

## Letter-Value boxplots (1)

* What don't we like about this plot?
* How hard is it to explain?

```{r lettervalue, fig.height=4, fig.width=8, cache=TRUE}
# Now add varied distribution geoms
library(lvplot)
gg_base + geom_lv(aes(fill = ..LV..)) + scale_fill_lv()

```

## Letter-Value boxplots (2)

* What don't we like about this plot?
* How hard is it to explain?

```{r lettervalue2, fig.height=4, fig.width=8, cache=TRUE}
# Now add varied distribution geoms
library(lvplot)
gg_base + geom_lv(aes(fill = ..LV..)) + 
  scale_fill_lv() + 
  coord_cartesian(ylim = c(-50, 500)) 

```

## Letter-Value boxplots (3)

* What don't we like about this plot?
* How hard is it to explain?

```{r lv3, fig.height=4, fig.width=8, cache=TRUE}
# Now add varied distribution geoms
library(lvplot)
gg_base + geom_lv(aes(fill = ..LV..)) + 
  scale_fill_lv() + 
  coord_cartesian(ylim = c(-50, 1500)) 

```

# Thursday Classes {data-background=#e8d725}


## Art Class

> - [What do you see?](images/sculpt.jpg){target="blank"}
> - [What about here?](images/sculpt_wide.jpg){target="blank"}

## The Wilderness of Data

<iframe width="860" height="515" src="https://www.youtube.com/embed/fTgvdTftXfI" frameborder="0" allow="autoplay; encrypted-media" allowfullscreen></iframe>


## Small Challenge

> - Use `geom_violin()` and `geom_quasirandom()` with the `ggplot2::mpg` data to show the mpg distribution by vehicle class.

```{r newname_code2, echo=FALSE, eval=FALSE}
library(ggbeeswarm)
library(lvplot)

mpg %>%
ggplot(aes(x = class, y = hwy)) +
  geom_violin() +
  labs(x = "Class", y = "Miles per gallon (highway)") +
  theme_bw()

mpg %>%
ggplot(aes(x = class, y = hwy, color = factor(round(displ)))) +
  geom_quasirandom() +
  scale_color_viridis_d() +
  labs(x = "Class", y = "Miles per gallon (highway)", color = "Displacement") +
  theme_bw() + theme(legend.position = "bottom")

```

## Thursday Task in class

<<<<<<< HEAD
> - I (or Cody) will work on this task with you in class for a large majority of the period.
> - 
=======
> * [link to last presentation](day_5.html#/displaying-distributions-of-multiple-groups-for-decision-making)

## Next Challenge

```{r newname_code2, echo=FALSE}
library(ggbeeswarm)
library(lvplot)

mpg %>%
ggplot(aes(x = class, y = hwy)) +
  geom_violin() +
  labs(x = "Class", y = "Miles per gallon (highway)") +
  theme_bw()

mpg %>%
ggplot(aes(x = class, y = hwy, color = factor(round(displ)))) +
  geom_quasirandom() +
  scale_color_viridis_d() +
  labs(x = "Class", y = "Miles per gallon (highway)", color = "Displacement") +
  theme_bw() + theme(legend.position = "bottom")

```
>>>>>>> 3555fbbcd42e43308a527a106f7c819389108e06
