---
title: "Getting into Data, dplyr and ggplot2"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      keep_md: true
      incremental: true
      theme: moon
      highlight: espresso
      center: true
      self_contained: false
      reveal_plugins: ["chalkboard"]
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        chalkboard:
          theme: whiteboard
          
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

#  How do we know when we have given voice to data?

## "The simple graph has brought more information to the data analyst's mind than any other device."

### John Tukey


## "The greatest value of a picture is when it forces us to notice what we never expected to see." 

### John Tukey

## Hans Rosling and Data Interaction

- I put them together, so that in each pair of country, one has twice the child mortality of the other. **And this means that it's much bigger a difference than the uncertainty of the data.**

- [I have shown that Swedish top students know statistically significantly less about the world than the chimpanzees.](https://www.youtube.com/embed/usdJgEwMinM?rel=0&amp;start=80)

- [It's a tremendous variation within Africa which we rarely often make -- that it's equal everything.](https://www.youtube.com/embed/usdJgEwMinM?rel=0&amp;start=570)

- [Now, this is, more or less, if you look at the average data of the countries -- they are like this. Now that's dangerous, to use average data, because there is such a lot of difference within countries.](https://www.youtube.com/embed/usdJgEwMinM?rel=0&amp;start=823)

# Wrangling Data

## library(dplyr)

> - `filter()`  - filter your data to a smaller set of important rows.
> - `arrange()` - Orginize the row order of my data
> - `select()`  - select specific columns to keep or remove 
> - `mutate()`  - add new mutated (changed) variables as columns to my data.
> - `summarise()` - build summaries of the columns specified
> - `group_by()`  - divide your data into groups. Often used with `summarise()`

## The pipe `%>%`

You can read it as a series of imperative statements: group, then summarise, then filter. As suggested by this reading, a good way to pronounce %>% when reading code is **"then"**.

* Behind the scenes, x %>% f(y) turns into f(x, y), and x %>% f(y) %>% g(z) turns into g(f(x, y), z) and so on. 
* You can use the pipe to rewrite multiple operations in a way that you can read left-to-right, top-to-bottom. 
* We'll use piping frequently from now on because it considerably improves the readability of code.

## Practice reading code

<small>
> - dat - is the data set of children from a longitudinal study over the first two years of life.
> - bf.type.4 - The breastfeeding grouping based on the first four months of breastfeeding.
> - wasting - is the grouping of children based on how underweight they are for their height.
</small>

With your table, write this code out in an english paragraph.

```{r, eval=FALSE}
#
#
#

dat %>%
  filter(!is.na(bf.type.4), bf.type.4 != "none", wasting != "no group", 
         month_of_age %in% c(1:6,seq(8,24, by = 2)), 
         !country %in% c("Brazil", "Peru", "South Africa", "Tanzania")) %>%
  mutate(`BF Status 4 months` = 
          factor(bf.type.4, levels = c("exclusive", "predominant", "partial")),
         days = month_of_age*30.25) 
#
#
#
```

# Visualizing Data

## The grammar of graphics

> - [An overview of the grammar](https://www.youtube.com/embed/uiTc55clwuA?rel=0)
> - [ggplot2 specifics](https://www.youtube.com/embed/PiY9hwOkL8U?rel=0)


## Cleveland's Examples

There were three democratic candidates.  We are going to use the following plots to help us understand the constituency that helped the winner in the primaries.

- [1984 Primaries](https://en.wikipedia.org/wiki/Democratic_Party_presidential_primaries,_1984)
- [Mondale, Hart, Jackson Visualization](../images/Cleveland_1_ok.png){target="blank"}
- [Better Mondale, Hart, Jackson Visualisation](../images/Cleveland_1_better.png){target="blank"}
- How much time do you think it took Bill Cleveland in th 80's to make each graph?



## Practice Reading Code

With your table, write this code out in an English paragraph  (same first part but now write a senetnece about the graphic portion).

```{r, eval=FALSE}
dat %>%
  filter(!is.na(bf.type.4), bf.type.4 != "none", wasting != "no group", 
         month_of_age %in% c(1:6,seq(8,24, by = 2)), 
         !country %in% c("Brazil", "Peru", "South Africa", "Tanzania")) %>%
  mutate(`BF Status 4 months` = 
          factor(bf.type.4, levels = c("exclusive", "predominant", "partial")),
         days = month_of_age*30.25) %>%
    ggplot(aes(x = factor(month_of_age, levels = 1:24), y = whz)) +
      geom_boxplot(outlier.color = NA) +
      facet_grid(wasting~`BF Status 4 months` , labeller = "label_both") +
      coord_cartesian(ylim = c(-4, 4)) +
      theme_bw() +
      labs(x = "Breastfeeding status at 4 months", 
           y = "WHZ", color = "Country")
```

## Copy DataCamp Iris Example

> - Let's copy their iris data example in the [ggplot2 specifics video](https://www.youtube.com/embed/PiY9hwOkL8U?start=141)

# Case Study 2

## Wealth and Life Expectancy

[Case Study 2](https://byuistats.github.io/M335/weekly_projects/cs02_details.html)

