---
title: "Big Data, Data Science, and Tools"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      lib_dir: externals
      keep_md: true
      incremental: true
      theme: black
      highlight: espresso
      center: true
      code_folding: hide
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        maxScale: 3
        margin: 0
params:
  day: 22
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(knitr)
library(stringr)

invisible(purl("../backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")


# case study completed
cso <- ceiling(params$day/2) - 1
csn <- ceiling(params$day/2) 

casename_old <-  paste0("cs-", str_pad(cso, 2, "left", "0"))
casename_new <-  paste0("cs-", str_pad(csn, 2, "left", "0"))

link_old <- paste0("> - [Case Study ", cso, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_old,"-",""), "_details.html)")
link_new <- paste0("> - [Case Study ", csn, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_new,"-",""), "_details.html)")

# How did we do?
hdwd <- "> - [How did we do?](https://github.com/BYUI335/hathaway)"

# current task
# 
taskname <- paste0("task-", str_pad(params$day, 2, "left", "0"))
link_task <- paste0("> - [Task ", params$day, "](https://byuistats.github.io/M335/class_tasks/", str_replace(taskname,"-",""), "_details.html)")
```

# Review

```{r csnew, ref.label=casename_new, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_new`


```{r task, ref.label=taskname, echo=FALSE, include=FALSE }
# For current task that is due
```

`r title.text`
`r link_task`


```{r stuff, echo=FALSE}
unlink("temp")
```


# Big Data Readings

## The Material

> - Questions about [Hadoop](https://www.youtube.com/watch?v=4DgTLaFNQq0&feature=youtu.be)?
> - Questions about [Spark](https://mapr.com/blog/spark-101-what-it-what-it-does-and-why-it-matters/)?
> - [Cleveland & Hafen Paper](http://onlinelibrary.wiley.com/doi/10.1002/sam.11242/epdf)

## Cleveland & Hafen Discussion

Let's move the tables around and have this conversation "book group" style.

# Using TrelliscopeJS

## Looking at an Example

[Housing Prices](http://hafen.github.io/trelliscopejs-demo/housing/)

## Loading Packages

```{r c1, eval=FALSE}

# devtools::install_github("hathawayj/buildings")
# library(buildings)
# devtools::install_github("hafen/trelliscopejs")
library(trelliscopejs)
library(tidyverse)
data(permits, package="buildings")
```
## Nesting Data

```{r c2, eval=FALSE}

#by state and county

by_stco <- permits %>%
  filter(StateAbbr %in% c("WA", "ID", "UT"), variable == "Single Family") %>%
  group_by(StateAbbr, countyname) %>%
  nest()

```

## Adding Plots

```{r c3, eval=FALSE}
by_stco <- by_stco %>% 
  mutate(
    panel = map_plot(data,
                     ~ ggplot(data = .x, aes(x = year, y = value)) +
                       geom_point() +
                       geom_line(color = "grey") +
                       #xlim(2000, 2011) + 
                       #ylim(0, 1250) +
                       theme_bw()
    ))
```

## Making the Magic

```{r c4, eval=FALSE}

# plot it
my_display <- tempfile()
by_stco %>%
  trelliscope("permits", nrow = 2, ncol = 7, 
              path = my_display, thumb = TRUE, width = 500)



```

# Spark and Big Data

## Using R with Spark

> - [Try out Sparklyr: R interface to Apache Spark](https://spark.rstudio.com)
>    - [Nice Rstudio blog post](https://blog.rstudio.com/2016/09/27/sparklyr-r-interface-for-apache-spark/)
>    - [Another example from H20](https://github.com/trestletech/user2016-sparklyr)
>    - [Build Histogram from Distributed data](https://github.com/rstudio/sparkDemos/blob/master/prod/presentations/cloudera/sqlvis_histogram.R)


