---
title: "Pulling Strings"
author: J. Hathaway
params:
  day: 12
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

if (params$day %% 2 == 0) md_intro_format <- "even_intro_format.Rmd"
if (params$day %% 2 == 1) md_intro_format <- "odd_intro_format.Rmd"

```

# Becoming the Critic.

```{r nextone}
vday <- params$day - 1
vlink <- paste0("http://www.perceptualedge.com/example", vday, ".php")
titlelink <- paste0('{data-background-iframe="', vlink, '"}')
```


```{r child=md_intro_format}

```


# Visualizing Impact

## A visualization and the steps

> - [Gun Deaths](http://guns.periscopic.com/?year=2013)

> 1. Be open to discovering new insights
> 2. Think big but start small
> 3. Design for your user
> 4. Prototype to identify needs (Sketch to code)
> 5. Obtain feedback early and often

"If I had asked my customers what they wanted they would have told me faster horses."

## Step 3. Design for your user

We explored treemaps and pie charts as ways to visualize the potential cost savings by product category. Lots of discrete clusters made pie charts ineffective. When we tested the treemaps, users found it difficult to arrive at a clear decision when comparing across product categories. Users also grappled to understand more complex visualizations as they were mostly accustomed to excel type visualizations.

## Conclusion

Successful visualizations consider user needs, business needs and the technology platform. It's easy to create visualizations that are interesting but not effective for the users consuming the insights. 

# Regular Expressions

## Some Background on RegEx

> - [History of RegEx](https://blog.staffannoteberg.com/2013/01/30/regular-expressions-a-brief-history/)

**A few jokes**

> - [Really](http://geek-and-poke.com/geekandpoke/2013/12/3/yesterdays-regex)
> - [Superheros](https://www.explainxkcd.com/wiki/images/7/7b/regular_expressions.png)

## Class Activity (RegEx)

**[temple data sealing activity](https://byuistats.github.io/M335/temple_sealings.html)**

> 1. Use regular expressions to fix the temple name key so they match in each data set and then join. 
> 2. With your final data make the announcement date a date value
> 3. Make a plot with announcement date on the x-axis and square footage on the y-axis

> - [str_replace_all()](http://stringr.tidyverse.org/reference/str_replace.html)
> - follow [link](https://www.rdocumentation.org/packages/stringi/versions/1.1.5/topics/stringi-search-regex) to regular expression information
> - now remove the trailing characters after Temple - [regex101](https://regex101.com/) or [regexr](https://regexr.com)

