---
title: "Moving Time Part II"
author: J. Hathaway
params:
  day: 18
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

if (params$day %% 2 == 0) md_intro_format <- "even_intro_format.Rmd"
if (params$day %% 2 == 1) md_intro_format <- "odd_intro_format.Rmd"

```

```{r child=md_intro_format}

```

# Visual Perception

## Rauser on Cholera

[Remembering the question: A cholera example](https://www.youtube.com/watch?v=-3dw09N5_Aw)

  - 3:00 What are the good methods he uses to provide background on the domain science?
  - 3:37 If we had to prove that cholera wasn't passed by the air what type of data would we need?
  - 4:52 Do you think this is compelling? 
  - 5:33 Can we do this experiment?
  - 7:22 The data scientist has to find the data.
  - 9:31 The data scientist has to give the data purpose.
  - 11:00 Finding the unique features provide the experimentation value. 

## Great Quotes

- Correlation does not imply causation... The most popular defense of tiny minds in the face of uncomfortable evidence.
- You are rewarded for finding answers to the "that's funny" statements.

## Why is this a poor example of non-aligned scales?

> - https://pix-media.priceonomics-media.com/blog/1103/image04b.png

# Remember and DataTables

## Remember the Goal

"The most exciting phrase to hear in science, the one that heralds new discoveries, is not 'Eureka!' but 'That's funny...'" -Isaac Asimov

> - [Remembering Good Principles](https://youtu.be/fSgEeI2Xpdc)
> - [Rauser view on time and data](https://www.youtube.com/embed/coNDCIMH8bk?start=628) - 10:28 to 17:50
> - [Statistical Tests](https://www.youtube.com/embed/5Dnw46eC-0o)


## library(DT) - DataTables

Look at the [DT: An R interface to the DataTables library](http://rstudio.github.io/DT/) website and find one or two modifications that you could make to your table output to move beyond the default.

> * Work as a table and push one file to R-Studio connect.
> * Make sure everyone at the table has the code saved on their computers.

```{r bob, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r bob2, eval=FALSE}
library(DT)
datatable(iris)
```
