---
title: "Understanding Time"
author: J. Hathaway
output: 
  revealjs::revealjs_presentation:
      lib_dir: externals
      keep_md: true
      incremental: true
      theme: black
      highlight: espresso
      center: true
      code_folding: hide
      reveal_options:
        previewLinks: true
        mouseWheel: true
        slideNumber: true
        maxScale: 3
        margin: 0
params:
  day: 14
  ptitle: true
  pbackground: true
  dtype: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(knitr)
library(stringr)

invisible(purl("../backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")


# case study completed
cso <- ceiling(params$day/2) - 1
csn <- ceiling(params$day/2) 

casename_old <-  paste0("cs-", str_pad(cso, 2, "left", "0"))
casename_new <-  paste0("cs-", str_pad(csn, 2, "left", "0"))

link_old <- paste0("> - [Case Study ", cso, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_old,"-",""), "_details.html)")
link_new <- paste0("> - [Case Study ", csn, "](https://byuistats.github.io/M335/weekly_projects/", str_replace(casename_new,"-",""), "_details.html)")

# How did we do?
hdwd <- "> - [How did we do?](https://github.com/BYUI335/hathaway)"

# current task
# 
taskname <- paste0("task-", str_pad(params$day, 2, "left", "0"))
link_task <- paste0("> - [Task ", params$day, "](https://byuistats.github.io/M335/class_tasks/", str_replace(taskname,"-",""), "_details.html)")
```

# Review

```{r csnew, ref.label=casename_new, echo=FALSE, include=FALSE }
# For case study due next Saturday
```

`r title.text`
`r link_new`


```{r task, ref.label=taskname, echo=FALSE, include=FALSE }
# For current task that is due
```

`r title.text`
`r link_task`


```{r stuff, echo=FALSE}
unlink("temp")
```


# Class Activity


## The Walmart March Visualization

> - [Small multiples and time](http://excelcharts.com/wp-content/uploads/2012/06/walmart-growth-micromaps1.png)
> - [Without spatial](http://excelcharts.com/wp-content/uploads/2012/06/walmart-reorderable-matrix.png)


## The Walmart Challenge

Ignoring the color.  Let's recreate this graphic.  

> - [Without spatial](http://excelcharts.com/wp-content/uploads/2012/06/walmart-reorderable-matrix.png)
> - [Walmart Openings csv](https://byuistats.github.io/M335/data/Walmart_store_openings.csv)

# Making new R package friends

## The challenge

1. Pick one of the R packages on the following slide
2. Read material on the R package
3. Build a working script that demonstrates the use of the R package.
4. Write up a short presentation on the package.

## The packages

- [rio: The double click of data import](https://cran.r-project.org/web/packages/rio/vignettes/rio.html#data_import)
- [janitor: making the cleaning easy](https://github.com/sfirke/janitor)
- [tidytext: helps for text mining](https://github.com/juliasilge/tidytext)
- [fst: yes it is fast](http://www.fstpackage.org/)
- [glue: why should we paste](https://github.com/tidyverse/glue)
- [reinstallr: getting your packages back](https://github.com/calligross/reinstallr)
- [multidplyr: we need more than one dplyr?](http://www.business-science.io/code-tools/2016/12/18/multidplyr.html)


