---
title: "Class Discussion Materials"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}

source("../scripts/build_dates.R")


```






## Weeks 1 & 2:  Introduction to R and Data Science

* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`

## Weeks 3 & 4: Programming in the Tidyverse

* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`

## Week 5: Handling Varied Data Types

* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`


## Week 6 & 7: Characters and RegEx

* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`

## Week 8 & 9: Dates and Time

* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`

## Week 10 & 11: Spatial

* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`

## Week 12 & 13: Finishing (Project and Semester Deliverables)

* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`
* **`r paste0(month(dates_class$start[pr]), "/", mday(dates_class$start[pr]), " (Day ", pr, ")")`:** [html](`r dates_class$url[pr]`){target="blank"} / [md](`r str_replace(dates_class$url[pr], ".html", ".md")`) / [rmd](`r str_replace(dates_class$url[pr], ".html", ".Rmd")`) `r pr <- pr + 1`


## Random Stuff

* [Spatial Class](spatial_class.html)
* [hathaway restaurant code](https://byuistats.github.io/M335/presentations_class/restaurants_idaho.html)
* [temple data sealing activity](temple_sealings.html)
* [Overview of Git and GitHub use in our course](git_335.html).  Please note the folder structure you need in your repository.
* [ggplot2 intro](https://stats.idre.ucla.edu/r/seminars/ggplot2_intro/): It has a nice example for `stat_summary()`
* [git command workflow](https://byuistats.github.io/M335/images/Git_workflow_diagram.png){target="blank"}
* [Data is Beautiful](https://np.reddit.com/r/dataisbeautiful/){target="blank"}