---
title: "Schedule"
params:
  dtype: background
  ptitle: FALSE
  pbackground: FALSE
output:
  html_document:  
    keep_md: TRUE 
    toc_float:
      collapsed: true    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r include=FALSE}
library(fullcalendar)

source("../scripts/build_dates.R")

```

# Calendar

The yellow boxes are the days we have class this semester.  The dark green boxes when work is due.

```{r, echo=FALSE, fig.width=8}
fullcalendar(dates_all, settings = list(firstDay = 1, header = FALSE, 
                                        height = 500, aspectRatio = 1.75,
                                        footer = list(right = "today prev,next, title"), titleFormat = ' MM-YYYY'))
```

<br>

---------


```{r purlstuff, message=FALSE, warning=FALSE, echo=FALSE }
library(knitr)
invisible(purl("backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")
day_seq <- task_due
```

# Details

## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs01, ref.label="cs-01", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task01, ref.label="task-01", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task02, ref.label="task-02", results="asis", echo=FALSE}
```

`r pr <- pr +1`

<!-- Case Study 2 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs02, ref.label="cs-02", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task03, ref.label="task-03", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task04, ref.label="task-04", results="asis", echo=FALSE}
```

`r pr <- pr +1`


<!-- Case Study 3 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs03, ref.label="cs-03", results="asis", echo=FALSE}
```


### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task05, ref.label="task-05", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task06, ref.label="task-06", results="asis", echo=FALSE}
```

`r pr <- pr +1`

<!-- Case Study 4 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs04, ref.label="cs-04", results="asis", echo=FALSE}
```



### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".",pr*2 - 1, ")" )` 

```{r task07, ref.label="task-07", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task08, ref.label="task-08", results="asis", echo=FALSE}
```

`r pr <- pr +1`

<!-- Case Study 5 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs05, ref.label="cs-05", results="asis", echo=FALSE}
```


### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task09, ref.label="task-09", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task10, ref.label="task-10", results="asis", echo=FALSE}
```


`r pr <- pr +1`



<!-- Case Study 6 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs06, ref.label="cs-06", results="asis", echo=FALSE}
```


### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task11, ref.label="task-11", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task12, ref.label="task-12", results="asis", echo=FALSE}
```

`r pr <- pr +1`

<!-- Case Study 7 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs07, ref.label="cs-07", results="asis", echo=FALSE}
```


### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task13, ref.label="task-13", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task14, ref.label="task-14", results="asis", echo=FALSE}
```

`r pr <- pr +1`


<!-- Case Study 8 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs08, ref.label="cs-08", results="asis", echo=FALSE}
```


### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task15, ref.label="task-15", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task16, ref.label="task-16", results="asis", echo=FALSE}
```

`r pr <- pr +1`


<!-- Case Study 9 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs09, ref.label="cs-09", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task17, ref.label="task-17", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task18, ref.label="task-18", results="asis", echo=FALSE}
```

`r pr <- pr +1`


<!-- Case Study 10 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs10, ref.label="cs-10", results="asis", echo=FALSE}
```


### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task19, ref.label="task-19", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task20, ref.label="task-20", results="asis", echo=FALSE}
```

`r pr <- pr +1`

<!-- Thanksgiving Week -->
<!-- Case Study 11 -->
<!-- ### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`) -->

<!-- ```{r child="weekly_projects/cs11_background.Rmd"} -->

<!-- ``` -->


<!-- #### `r paste(month(day_seq[vals[1]]),mday((day_seq[vals[1]])), sep = "/")` -->

<!-- #### `r paste(month(day_seq[vals[2]]),mday((day_seq[vals[2]])), sep = "/")` -->

<!-- `r # Need to uncomment pr` -->
<!-- `r #pr <- pr + 1` -->


<!-- Case Study 11 or 12 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs11, ref.label="cs-11", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task21, ref.label="task-21", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task22, ref.label="task-22", results="asis", echo=FALSE}
```


`r pr <- pr +1`


<!-- Case Study 12 or 13 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs12, ref.label="cs-12", results="asis", echo=FALSE}
```

### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task23, ref.label="task-23", results="asis", echo=FALSE}
```


### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task24, ref.label="task-24", results="asis", echo=FALSE}
```


`r pr <- pr +1`

<!-- Case Study 12 or 13 -->
## Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r paste(month(last_day_finals), mday(last_day_finals), sep="/")`)

```{r cs13, ref.label="cs-13", results="asis", echo=FALSE}
```




```{r, echo=FALSE}
unlink("temp")
```


