---
title: "Schedule"
params:
  dtype: background
  ptitle: FALSE
  pbackground: FALSE
output:
  html_document:  
    keep_md: TRUE 
    toc_float:
      collapsed: true    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r, include=FALSE}
library(lubridate)
library(calheatmapR)
library(timeDate)
library(stringr)
library(fullcalendar)
library(tidyverse)


# first_day <- mdy_h("09/12/2017 10", tz = "America/Denver")
# last_day <- mdy_h("12/12/2017 10", tz = "America/Denver")
# last_day_finals <- mdy("12/15/2017", tz = "America/Denver")
first_day <- mdy_h("01/09/2018 10", tz = "America/Denver") # should be a tuesday or thursday date.
last_day <- mdy_h("04/11/2018 10", tz = "America/Denver")
last_day_finals <- mdy("04/13/2018", tz = "America/Denver")

dayone_seq <-  seq(first_day, last_day, by = "weeks")
saturday_seq <- ceiling_date(dayone_seq, "week") - days(1)
saturday_seq <- saturday_seq[saturday_seq < last_day]

fday_name <- as.character(wday(first_day, label = TRUE))

check_day <- first_day


if (fday_name == "Tues") {
  day(check_day) <- day(check_day) + 2  
  daytwo_seq = seq( check_day, last_day, by = "weeks")
} 
if (fday_name == "Thurs") {
  day(check_day) <- day(check_day) + 5  
  daytwo_seq = seq(check_day , last_day, by = "weeks")
}
  

day_seq = sort(c(dayone_seq,daytwo_seq))

first_week <- week(first_day)
last_week <-  week(last_day)

# holidays

if (month(first_day) != 1){
  
thanksgiving <- ymd(date(holiday(year = getRmetricsOptions("currentYear"), Holiday = "USThanksgivingDay")))

thanksgiving_b <- thanksgiving
thanksgiving_a <- thanksgiving
day(thanksgiving_b) <- day(thanksgiving_b) - 1  
day(thanksgiving_a) <- day(thanksgiving_a) + 1
thanksgiving <-  c(thanksgiving_b, thanksgiving, thanksgiving_a)

pioneer <- mdy(paste("7/24/", getRmetricsOption("currentYear"),sep = ""))


holidays <- c(date(holiday(year = getRmetricsOptions("currentYear"), Holiday = "USMLKingsBirthday")),
  date(holiday(year = getRmetricsOptions("currentYear"), Holiday = "USPresidentsDay")),
  date(holiday(year = getRmetricsOptions("currentYear"), Holiday = "USMemorialDay")),
  date(holiday(year = getRmetricsOptions("currentYear"), Holiday = "USIndependenceDay")),
  pioneer,
  date(holiday(year = getRmetricsOptions("currentYear"), Holiday = "USLaborDay")),
  date(holiday(year = getRmetricsOptions("currentYear"), Holiday = "USColumbusDay")),
  date(holiday(year = getRmetricsOptions("currentYear"), Holiday = "USVeteransDay")),
  thanksgiving)
  
day_seq <- day_seq[!yday(day_seq) %in% yday(holidays)]

} # end if to not run for winter semester

no_saturday <- ceiling_date(day_seq[c(diff(wday(day_seq)),-2) == 0], "week") - days(1)

saturday_seq <- saturday_seq[!saturday_seq %in% no_saturday]

day_map <- day_seq

day_seq <- day_seq[c(diff(wday(day_seq)),-2) != 0]

task_due <- day_seq - days(1)
task_due <- task_due[1:24]

# day_seq has the class days
# saturday_seq has the saturdays during the semester
# task_due has the date that the task is due
# 

# finds the case study md file and pulls the task and title
body_lines <-  read_lines("backgrounds.md")
# title pulled
titles <-  body_lines[str_detect(body_lines, "##")] %>% 
  str_replace("## ", "") %>% 
  str_replace("Case Study", "CS") %>%
  str_trim()
numbers <- str_split_fixed(titles, ":", 2)[,1] %>% paste0(" Due")
links <- body_lines[str_detect(body_lines, " \\* \\[Details\\]")]  %>% 
  str_replace(" \\* \\[Details\\]", "") %>%
  str_replace("\\(", "") %>% str_replace("\\)", "") %>%
  str_trim()
lesson_links <- paste0("https://byuistats.github.io/M335/presentations_class/day_", 1:length(day_seq) , ".html")

links <- paste0("https://byuistats.github.io/M335/", links)

dates_due <- data.frame(title = numbers, start = paste(floor_date(c(task_due, saturday_seq), unit = "days")), 
                          url = links, color = "darkgreen")
dates_class <- data.frame(title = "Class", start = paste(floor_date(c(day_seq), unit = "days")), 
                          url = lesson_links, color = "gold")

dates_all <- bind_rows(dates_due, dates_class)
pr <- 1

```

### Calendar

The yellow boxes are the days we have class this semester.  The dark green boxes when work is due.


```{r, shedulemap, echo=FALSE}

date.list <-  as.list( c(rep(1, length(day_seq)), rep(50, length(saturday_seq)), rep(50, length(task_due))))
names(date.list) <- c(as.numeric( ceiling_date(day_seq)), as.numeric(as.POSIXct(saturday_seq)), 
                      as.numeric( ceiling_date(task_due)))


calheatmapR(data = date.list, height = 300) %>%
  chDomain(domain = "month", subDomain = "day", start = min(day_seq),
           range = 4, cellSize = 30, cellPadding = 4, gutter = 15, subDomainTextFormat = "%d") %>%
  chLegend(display = FALSE)



```





```{r, echo=FALSE, fig.width=8}
fullcalendar(dates_all, settings = list(firstDay = 1, header = FALSE, height = 500, aspectRatio = 1.75,
                                        footer = list(right = "today prev,next")))
```

<br>

---------


```{r purlstuff, message=FALSE, warning=FALSE, echo=FALSE }
library(knitr)
invisible(purl("backgrounds.Rmd", output = "temp", quiet = TRUE))
read_chunk("temp")
day_seq <- task_due
```

   
   
   
   
   


### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs01, ref.label="cs-01", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task01, ref.label="task-01", results="asis", echo=FALSE}
```



#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task02, ref.label="task-02", results="asis", echo=FALSE}
```




`r pr <- pr +1`

<!-- Case Study 2 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs02, ref.label="cs-02", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task03, ref.label="task-03", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task04, ref.label="task-04", results="asis", echo=FALSE}
```

`r pr <- pr +1`


<!-- Case Study 3 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs03, ref.label="cs-03", results="asis", echo=FALSE}
```


#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task05, ref.label="task-05", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task06, ref.label="task-06", results="asis", echo=FALSE}
```

`r pr <- pr +1`

<!-- Case Study 4 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs04, ref.label="cs-04", results="asis", echo=FALSE}
```



#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".",pr*2 - 1, ")" )` 

```{r task07, ref.label="task-07", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task08, ref.label="task-08", results="asis", echo=FALSE}
```

`r pr <- pr +1`

<!-- Case Study 5 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs05, ref.label="cs-05", results="asis", echo=FALSE}
```


#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task09, ref.label="task-09", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task10, ref.label="task-10", results="asis", echo=FALSE}
```


`r pr <- pr +1`



<!-- Case Study 6 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs06, ref.label="cs-06", results="asis", echo=FALSE}
```


#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task11, ref.label="task-11", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task12, ref.label="task-12", results="asis", echo=FALSE}
```

`r pr <- pr +1`

<!-- Case Study 7 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs07, ref.label="cs-07", results="asis", echo=FALSE}
```


#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task13, ref.label="task-13", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task14, ref.label="task-14", results="asis", echo=FALSE}
```

`r pr <- pr +1`


<!-- Case Study 8 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs08, ref.label="cs-08", results="asis", echo=FALSE}
```


#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task15, ref.label="task-15", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task16, ref.label="task-16", results="asis", echo=FALSE}
```

`r pr <- pr +1`


<!-- Case Study 9 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs09, ref.label="cs-09", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task17, ref.label="task-17", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task18, ref.label="task-18", results="asis", echo=FALSE}
```

`r pr <- pr +1`


<!-- Case Study 10 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs10, ref.label="cs-10", results="asis", echo=FALSE}
```


#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task19, ref.label="task-19", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task20, ref.label="task-20", results="asis", echo=FALSE}
```

`r pr <- pr +1`

<!-- Thanksgiving Week -->
<!-- Case Study 11 -->
<!-- ### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`) -->

<!-- ```{r child="weekly_projects/cs11_background.Rmd"} -->

<!-- ``` -->


<!-- #### `r paste(month(day_seq[vals[1]]),mday((day_seq[vals[1]])), sep = "/")` -->

<!-- #### `r paste(month(day_seq[vals[2]]),mday((day_seq[vals[2]])), sep = "/")` -->

<!-- `r # Need to uncomment pr` -->
<!-- `r #pr <- pr + 1` -->


<!-- Case Study 11 or 12 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs11, ref.label="cs-11", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task21, ref.label="task-21", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task22, ref.label="task-22", results="asis", echo=FALSE}
```


`r pr <- pr +1`


<!-- Case Study 12 or 13 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r d <- ceiling_date(day_seq[vals[1]], "weeks")- days(1); paste(month(d), mday(d), sep="/")`)

```{r cs12, ref.label="cs-12", results="asis", echo=FALSE}
```

#### `r paste0(month(day_seq[vals[1]]), "/", mday((day_seq[vals[1]])), " (",pr,".", pr*2 - 1, ")" )` 

```{r task23, ref.label="task-23", results="asis", echo=FALSE}
```


#### `r paste0(month(day_seq[vals[2]]), "/", mday((day_seq[vals[2]])), " (", pr, ".", pr*2, ")")`

```{r task24, ref.label="task-24", results="asis", echo=FALSE}
```


`r pr <- pr +1`

<!-- Case Study 12 or 13 -->
### Case Study `r vals = c(pr*2-1,pr*2); pr` (Due `r paste(month(last_day_finals), mday(last_day_finals), sep="/")`)

```{r cs13, ref.label="cs-13", results="asis", echo=FALSE}
```




```{r, echo=FALSE}
unlink("temp")
```


