---
title: "I am a Data Scientist"
output:
  html_document:
    toc: true
    keep_md: true
    variant: markdown_github  
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

### Background / Purpose

Each of you will be responsible to create a data driven question, find the data to answer this question, and build a visual analysis that answers your question with data.  A few notes on this project;

1. This project is done over a semester.  If you try to complete it during the last few weeks of the semester you will not succeed.
2. The data science majors will submit this as a part of their degree completion.  This project could be a great stepping stone for your senior project.
3. I would highly recommend that you do this project well and make it public on your Github repository to demonstrate to employers that you have data programming skills.

### Tasks

```{r results="asis", echo=FALSE}
cat("
<style>
ul {
   color: black;
   list-style-type: none;
   list-style-position: outside;

}

</style>
")
```

The semester project has three different tasks that need to be completed in order to fulfill the task - **question generation, data acquisition, and answer development**.

#### Question Generation & Data Acquisition

```{r results="asis", echo=FALSE, message=FALSE, warning=FALSE}
source("../scripts/md_bullets.R")
library(readxl)
library(dplyr)
readings <- read_excel(path = "../tasks_reading.xlsx", sheet = "Reading")
cases <- read_excel(path = "../tasks_reading.xlsx", sheet = "CaseStudies")
tasks <- read_excel(path = "../tasks_reading.xlsx", sheet = "Tasks")


cat("
<style>
ul {
   color: black;
   list-style-type: none;
   list-style-position: outside;

}

</style>
")
```


```{r, results="asis", echo=FALSE}

md_bullet(cases, group = list("Number" = 1), lines.keep = 1:3)
cat("\n\n")
cat("--------\n\n")
md_bullet(tasks, group = list("Number" = 3), lines.keep = 2:5)

cat("\n")

```


#### Answer Development


```{r, results="asis", echo=FALSE}

cat("\n\n")
md_bullet(tasks, group = list("Number" = 7), lines.keep = 2:8)
cat("\n\n")
cat("--------\n")
md_bullet(cases, group = list("Number" = 12), lines.keep = 1:8)


```