---
title: "Getting Sta**R**ted"
output: html_document
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R, R-Studio, .Rmd files, and .R scripts 

We will need to install [R](https://www.r-project.org/about.html){target="blank"}, R-Studio, and get comfortable with `.Rmd` files and `.R` files.

**R**

* The R website is where we can go to find the [latest version](http://ftp.osuosl.org/pub/cran/){target="blank"} to download for your particular operation system.
* Here is a video for [Mac users](http://youtu.be/Icawuhf0Yqo) and [Windows users](http://youtu.be/mfGFv-iB724). There is also a Linux version of R as well.

**.R Scripts**

* `.R` script files are the typical file type for saving your `R` scripts. This is often the file I start with for any analysis.  In fact, if you have experience with `.Rmd` files, you can write an `.R` script in such a way that it can be built into an html page like an `.Rmd` file.  See [here](http://brooksandrew.github.io/simpleblog/articles/render-reports-directly-from-R-scripts/).

**R-Studio & Rmd Files**

* R-Studio is a great software to facilitate the use of R (and many other things). We will use R-Studio heavily in this course!  Please download [R-Studio](https://www.rstudio.com/products/rstudio/download/).
* `.Rmd` files are the passport to a full space of data presentation opportunities.  Here is an [overview of R Markdown and its use in R-Studio](https://shiny.rstudio.com/articles/rmarkdown.html). Finally, here is a [short tutorial](rmarkdown_help.html) to get yourself up and running with R Markdown.

**R Packages**

* For your first package installation lets install `swirl`. This package will give you a good overview of R and it's base coding methods. After you follow [this guide](http://swirlstats.com/students.html), run `install_from_swirl("Data Analysis")` and `install_from_swirl("R Programming")`
   * Your first path for course tasks is to go through the modules of the "R Programming" course. Each of them should take 10-20 minutes.
   * Or you could go through [this free course](http://tryr.codeschool.com) 
   
## R Help Files

* [RDocumentation](https://www.rdocumentation.org/){target="blank"}

## R-Studio and Workflow

This section was lifted from work done by [jennybc](https://github.com/jennybc)'s development of [STAT545](https://github.com/STAT545-UBC).

```{r child="block002_hello-r-workspace-wd-project.rmd"}

```



