---
title: "Task List Form"
params:
  dtype: background
  pbackground: FALSE
  ptitle: FALSE
output:
  html_document:
    keep_md: yes
    toc_float:
      collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
md_bullet <- mean  # junk line to stop coding error from showing up.  Is overwritten by source next line.
source("../scripts/md_bullets.R")
library(readxl)
library(dplyr)
library(stringr)

cases <- read_excel(path = "../tasks_reading.xlsx", sheet = "CaseStudies")
tasks <- read_excel(path = "../tasks_reading.xlsx", sheet = "Tasks")
number = 1 # case study starting number
dnumber = 1

fname = paste("cs", str_pad(number, 2, "left", "0" ) , "_details.html", sep = "")
text <- paste("#### [Case Study ", number, "](", file.path("weekly_projects", fname), ")\n\n", sep = "")

fname_c = paste("task", str_pad(dnumber, 2, "left", "0" ) , "_details.html", sep = "")
text_c <- paste("#### [Class Task ", dnumber, "](", file.path("class_tasks", fname), ")\n\n", sep = "")



```

```{r, results="asis"}
cat("
<style>
ul {
   color: black;
   list-style-type: none;
   list-style-position: outside;

}

</style>
")
```

This page is provided to give you a one-page view of your task completion throughout the semester.  You can edit the `.md` file in your repository from `* [ ] blah blah blah` to `* [x] blah blah blah` to show the task as completed. You can see a [one-page view of all task backgrounds](backgrounds.html){target="blank"} as well.

**The mapping of tasks to a final grade is listed in [Syllabus::Competency Scale](syllabus.html#competency_scale)**

## Semester Deliverables

#### [Semester Project](project.html)

The deliverables for your [semester project](project.html) are assigned in [case study 1](weekly_projects/cs01_details.html) and [case study 12](weekly_projects/cs12_details.html). However you should keep a steady workflow on this project throughout the semester.  

#### [Leadership](teamlead.html)

Leadership in data science requires you to be prepared to answer the clients questions when the team meeting is scheduled.  We are treating class like the team meeting and you need to be [prepared to answer](cheating.html) and ask questions about the driving objectives from the client.

##### Data Science Leader (A level)

* [ ] Be the [team lead](teamlead.html) of the Tuesday case study presentation at least 3 times.
* [ ] Complete at least 18 class task [on time](cheating.html).
* [ ] Complete at least 10 case studies [on time](cheating.html).

##### Data Science Supporter (B level)

* [ ] Be the [team lead](teamlead.html) of the Tuesday case study presentation at least 2 times.
* [ ] Complete at least 12 class task on time.
* [ ] Complete at least 6 case studies on time.

##### Data Science Wannabe (C level)

* [ ] Be the [team lead](teamlead.html) of the Tuesday case study presentation at least 1 time.
* [ ] Complete at least 8 class task on time.
* [ ] Complete at least 4 case studies on time.

#### [Portfolio](weekly_projects/cs13_details.html)

[Case study 13](weekly_projects/cs13_details.html) provides the checklist items for your portfolio. This portfolio package will be the basis of your final grade. 

```{r, results="asis", echo=FALSE}
md_bullet(cases, group = list("Number" = 13))

```

#### Coding Challenge

On the last day of class each of you will have the 1.5 hours of class to complete a coding challenge.  You will not be able to work with others, but will be able to ask questions of the teacher in class. The coding challenge will use the techniques and programming developed from the course.

1. **You must pass the challenge to keep grade earned from the [completed tasks](https://byuistats.github.io/M335/syllabus.html#competency_scale).**
2. Failure to pass the challenge will lower your grade 1-2 steps.

## Weekly Case Studies

```{r results="asis"}
class_cs <- expression({
  # write current task header and link then list tasks
  cat(text)
  md_bullet(cases, group = list("Number" = number))
  cat("\n\n")
  # Step to the next task and header creation
  number <- number + 1
  fname = paste("cs", str_pad(number, 2, "left", "0" ) , "_details.html", sep = "")
  text <- paste("#### [Case Study ", number, "](", file.path("weekly_projects", fname), ")\n\n", sep = "")

})

for(i in 1:13){
eval(class_cs)  
}

```

## Daily Class Tasks


```{r results="asis"}
class_task <- expression({
  # write current task header and link then list tasks
  cat(text_c)
  md_bullet(tasks, group = list("Number" = dnumber))
  cat("\n\n")
  # Step to the next task and header creation
  dnumber <- dnumber + 1
  fname_c = paste("task", str_pad(dnumber, 2, "left", "0" ) , "_details.html", sep = "")
  text_c <- paste("#### [Class Task ", dnumber, "](", file.path("class_tasks", fname_c), ")\n\n", sep = "")

})

for(i in 1:24){
if (i == 1) cat(paste0("### Tasks 1 - 12\n\n")) 
if (i == 13) cat(paste0("### Tasks 13 -24\n\n")) 
eval(class_task)  
}

```
