---
title: "Task List Form"
params:
  dtype: background
  pbackground: FALSE
  ptitle: FALSE
output:
  html_document:
    keep_md: yes
    toc_float:
      collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
md_bullet <- mean  # junk line to stop coding error from showing up.  Is overwritten by source next line.
source("../scripts/md_bullets.R")
library(readxl)
library(dplyr)
library(stringr)

cases <- read_excel(path = "../tasks_reading.xlsx", sheet = "CaseStudies")
tasks <- read_excel(path = "../tasks_reading.xlsx", sheet = "Tasks")
number = 1 # case study starting number
dnumber = 1

fname = paste("cs", str_pad(number, 2, "left", "0" ) , "_details.html", sep = "")
text <- paste("#### [Case Study ", number, "](", file.path("weekly_projects", fname), ")\n\n", sep = "")

fname_c = paste("task", str_pad(dnumber, 2, "left", "0" ) , "_details.html", sep = "")
text_c <- paste("#### [Class Task ", dnumber, "](", file.path("class_tasks", fname), ")\n\n", sep = "")



```

```{r, results="asis"}
cat("
<style>
ul {
   color: black;
   list-style-type: none;
   list-style-position: outside;

}

</style>
")
```

This page is provided to give you a one-page view of your task completion throughout the semester.  You can edit the `.md` file in your repository from `* [ ] blah blah blah` to `* [x] blah blah blah` to show the task as completed. You can see a [one-page view of all task backgrounds](backgrounds.html){target="blank"} as well.

## Semester Deliverables

#### [Semester Project](project.html)

The deliverables for your [semester project](project.html) are assigned in [case study 9](weekly_projects/cs09_details.html) and [case study 12](weekly_projects/cs12_details.html). However you should keep a steady workflow on this project throughout the semester.  

#### [Leadership](leadership.html)

* [ ] Complete the class task before class starts
* [ ] Be a class lead during class (complete at least one of the following)
    * [ ] Supporting other students that need help getting through the last difficulties they had with the task
    * [ ] Presenting key coding methods or steps to the entire class
* [ ] Complete this task 12 times during the semester. 

#### [Portfolio](weekly_projects/cs13_details.html)

[Case study 13](weekly_projects/cs13_details.html) provides the checklist items for your portfolio. This portfolio package will be the basis of your final grade.  

## Weekly Case Studies

```{r results="asis"}
class_cs <- expression({
  # write current task header and link then list tasks
  cat(text)
  md_bullet(cases, group = list("Number" = number))
  cat("\n\n")
  # Step to the next task and header creation
  number <- number + 1
  fname = paste("cs", str_pad(number, 2, "left", "0" ) , "_details.html", sep = "")
  text <- paste("#### [Case Study ", number, "](", file.path("weekly_projects", fname), ")\n\n", sep = "")

})

for(i in 1:13){
eval(class_cs)  
}

```

## Daily Class Tasks


```{r results="asis"}
class_task <- expression({
  # write current task header and link then list tasks
  cat(text_c)
  md_bullet(tasks, group = list("Number" = dnumber))
  cat("\n\n")
  # Step to the next task and header creation
  dnumber <- dnumber + 1
  fname_c = paste("task", str_pad(dnumber, 2, "left", "0" ) , "_details.html", sep = "")
  text_c <- paste("#### [Class Task ", dnumber, "](", file.path("class_tasks", fname_c), ")\n\n", sep = "")

})

for(i in 1:24){
if (i == 1) cat(paste0("### Tasks 1 - 12\n\n")) 
if (i == 13) cat(paste0("### Tasks 13 -24\n\n")) 
eval(class_task)  
}

```
