---
title: "Temple Data Sealings"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

You can get the `.Rmd` file this [this link](temple_sealings.Rmd)

# Loading my R packages

```{r, packages}
#install.packages('htmltab')
# https://cran.r-project.org/web/packages/htmltab/vignettes/htmltab.html
library(htmltab)
library(reshape2)
library(tidyverse)
library(readr)
library(purrr)
library(lubridate)
library(ggrepel)
library(downloader)

# has functions kml_coordinate, kml_points, kml_polygons
source("https://gist.githubusercontent.com/briatte/18a4d543d1ccca194b2a03ac512be2b4/raw/5cd241ab780a33ec9a3ae6297a48f9035cda811d/get_points.r")

```

# Reading in raw data

```{r, loadingdata}
#kml file download http://ldschurchtemples.org/maps/
bob <- tempfile()
download("http://ldschurchtemples.org/maps/downloads/kml.php", bob)
temple.locs <- kml_points(bob) %>% select(name, longitude, latitude)

url_size <- "http://ldschurchtemples.org/statistics/dimensions/"
url_time <- "http://ldschurchtemples.org/statistics/timelines/"

dimensions <- htmltab(doc = url_size, 2) %>% as.tibble() 

times_AnGrbr <- htmltab(doc = url_time, 3) %>% select(-Duration) %>% as.tibble() 
times_GrbrDed <- htmltab(doc = url_time, 4) %>% select(-Duration) %>% as.tibble()
```

The [ldschurchtemples.org](http://ldschurchtemples.org/) has some nice data on LDS temples.  We will be using the following webpages to get location, size and timelines.

* [location](http://ldschurchtemples.org/maps/){target="blank"}
* [dimensions](http://ldschurchtemples.org/statistics/dimensions/){target="blank"}
* [timelines](http://ldschurchtemples.org/statistics/timelines/){target="blank"}

# Your Goal

Merge all four data sets into a table that looks like the table below.  **Note that this activity is teaching how to merge data sets and check for poor merges.**


|Temple                    |  longitude|   latitude|OrdinanceRooms |SealingRooms | SquareFootage|Announced  |Ground.Broken |Dedicated  |
|:-------------------------|----------:|----------:|:--------------|:------------|-------------:|:----------|:-------------|:----------|
|Aba Nigeria Temple        |   7.356719|   5.147644|2              |2            |         11500|2000-04-02 |2002-02-23    |2005-08-07 |
|Accra Ghana Temple        |  -0.193706|   5.567490|2              |2            |         17500|1998-02-16 |2001-11-16    |2004-01-11 |
|Adelaide Australia Temple | 138.635002| -34.892473|2              |2            |         10700|1999-03-17 |1999-05-29    |2000-06-15 |
